---
title: "Exploratory Data Analysis"
author: "Beast"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false
  pdf_document:
    toc: true
subtitle: Dalton & Madilin Super Document
mainfont: TimesNewRoman
sansfont: TimesNewRoman
monofont: TimesNewRoman
---

#### Load Relevant R Libraries
```{r warning=FALSE, message=FALSE}
library(rmarkdown); library(knitr); library(moments);library(mdsr) 
library(scatterplot3d); library(corrplot); library(pso);library(usethis)
library(psych); library(GPArotation); library(lavaan);library(here)
library(haven);library(tidyverse);library(tidyverse);library(ggplot2)
```

### Data Cleaning

#### Importing
```{r}
# Demographics
Demographics2011 <- read_xpt("Data 2011-12/DEMO_G.xpt") 
Demographics2013 <- read_xpt("Data 2013-14/DEMO_H.xpt") 
Demographics2015 <- read_xpt("Data 2015-16/DEMO_I.xpt")
Demographics2017 <- read_xpt("Data 2017-18/DEMO_J.xpt") 
Demographics2021 <- read_xpt("Data Aug2021-Aug2022/DEMO_L.xpt")
DemographicsPP2017 <- read_xpt("Data PP2017-20/P_DEMO.xpt")

# Examination
BloodPressure2011 <- read_xpt("Data 2011-12/BPX_G.xpt")
BloodPressure2013 <- read_xpt("Data 2013-14/BPX_H.xpt")
BloodPressure2015 <- read_xpt("Data 2015-16/BPX_I.xpt")
BloodPressure2017 <- read_xpt("Data 2017-18/BPX_J.xpt")
BloodPressure2021 <- read_xpt("Data Aug2021-Aug2022/BPXO_L.xpt")
BloodPressureP2017 <- read_xpt("Data PP2017-20/P_BPXO.xpt")

BodyMeasurements2011 <- read_xpt("Data 2011-12/BMX_G.xpt")
BodyMeasurements2013 <- read_xpt("Data 2013-14/BMX_H.xpt")
BodyMeasurements2015 <- read_xpt("Data 2015-16/BMX_I.xpt")
BodyMeasurements2017 <- read_xpt("Data 2017-18/BMX_J.xpt")
BodyMeasurements2021 <- read_xpt("Data Aug2021-Aug2022/BMX_L.xpt")
BodyMeasurementsP2017 <- read_xpt("Data PP2017-20/P_BMX.xpt")

# Lab
TotalChol2011 <- read_xpt("Data 2011-12/TCHOL_G.xpt")
TotalChol2013 <- read_xpt("Data 2013-14/TCHOL_H.xpt")
TotalChol2015 <- read_xpt("Data 2015-16/TCHOL_I.xpt")
TotalChol2017 <- read_xpt("Data 2017-18/TCHOL_J.xpt")
TotalChol2021 <- read_xpt("Data Aug2021-Aug2022/TCHOL_L.xpt")
TotalCholP2017 <- read_xpt("Data PP2017-20/P_TCHOL.xpt")

HDL_Chol2011 <- read_xpt("Data 2011-12/HDL_G.xpt")
HDL_Chol2013 <- read_xpt("Data 2013-14/HDL_H.xpt")
HDL_Chol2015 <- read_xpt("Data 2015-16/HDL_I.xpt")
HDL_Chol2017 <- read_xpt("Data 2017-18/HDL_J.xpt")
HDL_Chol2021 <- read_xpt("Data Aug2021-Aug2022/HDL_L.xpt")
HDL_CholP2017 <- read_xpt("Data PP2017-20/P_HDL.xpt")

LDL_Tri_Chol2011 <-read_xpt("Data 2011-12/TRIGLY_G.xpt")
LDL_Tri_Chol2013 <-read_xpt("Data 2013-14/TRIGLY_H.xpt")
LDL_Tri_Chol2015 <-read_xpt("Data 2015-16/TRIGLY_I.xpt")
LDL_Tri_Chol2017 <-read_xpt("Data 2017-18/TRIGLY_J.xpt")
LDL_Tri_Chol2021 <-read_xpt("Data Aug2021-Aug2022/TRIGLY_L.xpt")
LDL_Tri_CholP2017 <-read_xpt("Data PP2017-20/P_TRIGLY.xpt")

GLYP2013 <- read_xpt("Data 2013-14/SSGLYP_H.xpt")
GLYP2015 <- read_xpt("Data 2015-16/SSGLYP_I.xpt")
GLYP2017 <- read_xpt("Data 2017-18/SSGLYP_J.xpt")

Insulin2013 <- read_xpt("Data 2013-14/INS_H.xpt")
Insulin2015 <- read_xpt("Data 2015-16/INS_I.xpt")
Insulin2017 <- read_xpt("Data 2017-18/INS_J.xpt")
Insulin2021 <- read_xpt("Data Aug2021-Aug2022/INS_L.xpt")
InsulinP2017 <- read_xpt("Data PP2017-20/P_INS.xpt")

Metals2011 <-read_xpt("Data 2011-12/UHM_G.xpt")
Metals2013 <-read_xpt("Data 2013-14/UM_H.xpt")
Metals2015 <-read_xpt("Data 2015-16/UM_I.xpt")
Metals2017 <-read_xpt("Data 2017-18/UM_J.xpt")
Metals2021 <-read_xpt("Data Aug2021-Aug2022/PBCD_L.xpt")
MetalsP2017 <-read_xpt("Data PP2017-20/P_UM.xpt")

PFAs2011 <-read_xpt("Data 2011-12/PFC_G.xpt")
PFAs2013 <-read_xpt("Data 2013-14/SSPFSU_H.xpt")
PFAs2015 <-read_xpt("Data 2015-16/PFAS_I.xpt")
PFAs2017 <-read_xpt("Data 2017-18/PFAS_J.xpt")
PFAsP2017 <-read_xpt("Data PP2017-20/P_PFAS.xpt")

Hormones2011 <- read_xpt("Data 2011-12/TST_G.xpt")
Hormones2013 <- read_xpt("Data 2013-14/TST_H.xpt")
Hormones2015 <- read_xpt("Data 2015-16/TST_I.xpt")
Hormones2017 <- read_xpt("Data 2017-18/SSTST_J.xpt")
Hormones2021 <- read_xpt("Data Aug2021-Aug2022/TST_L.xpt")
HormonesP2017 <- read_xpt("Data PP2017-20/P_TST.xpt")

# Questionnaire 
DiabetesQ2011 <- read_xpt("Data 2011-12/DIQ_G.xpt")
DiabetesQ2013 <- read_xpt("Data 2013-14/DIQ_H.xpt")
DiabetesQ2015 <- read_xpt("Data 2015-16/DIQ_I.xpt")
DiabetesQ2017 <- read_xpt("Data 2017-18/DIQ_J.xpt")
DiabetesQ2021 <- read_xpt("Data Aug2021-Aug2022/DIQ_L.xpt")
DiabetesQP2017 <- read_xpt("Data PP2017-20/P_DIQ.xpt")

IncomeQ2011 <- read_xpt("Data 2011-12/INQ_G.xpt")
IncomeQ2013 <- read_xpt("Data 2013-14/INQ_H.xpt")
IncomeQ2015 <- read_xpt("Data 2015-16/INQ_I.xpt")
IncomeQ2017 <- read_xpt("Data 2017-18/INQ_J.xpt")
IncomeQ2021 <- read_xpt("Data Aug2021-Aug2022/INQ_L.xpt")
IncomeQP2017 <- read_xpt("Data PP2017-20/P_INQ.xpt")

MedicalCondnsQ2011 <- read_xpt("Data 2011-12/MCQ_G.xpt")
MedicalCondnsQ2013 <- read_xpt("Data 2013-14/MCQ_H.xpt")
MedicalCondnsQ2015 <- read_xpt("Data 2015-16/MCQ_I.xpt")
MedicalCondnsQ2017 <- read_xpt("Data 2017-18/MCQ_J.xpt")
MedicalCondnsQ2021 <- read_xpt("Data Aug2021-Aug2022/MCQ_L.xpt")
MedicalCondnsQP2017 <- read_xpt("Data PP2017-20/P_MCQ.xpt")

MentalHealthQ2011 <- read_xpt("Data 2011-12/DPQ_G.xpt")
MentalHealthQ2013 <- read_xpt("Data 2013-14/DPQ_H.xpt")
MentalHealthQ2015 <- read_xpt("Data 2015-16/DPQ_I.xpt")
MentalHealthQ2017 <- read_xpt("Data 2017-18/DPQ_J.xpt")
MentalHealthQ2021 <- read_xpt("Data Aug2021-Aug2022/DPQ_L.xpt")
MentalHealthQP2017 <- read_xpt("Data PP2017-20/P_DPQ.xpt")

PestisideQ2011 <- read_xpt("Data 2011-12/PUQMEC_G.xpt")
PestisideQ2013 <- read_xpt("Data 2013-14/PUQMEC_H.xpt")
PestisideQ2015 <- read_xpt("Data 2015-16/PUQMEC_I.xpt")
PestisideQ2017 <- read_xpt("Data 2017-18/PUQMEC_J.xpt")
PestisideQ2021 <- read_xpt("Data Aug2021-Aug2022/PUQMEC_L.xpt")
PestisideQP2017 <- read_xpt("Data PP2017-20/P_PUQMEC.xpt")

PhysicalActQ2011 <- read_xpt("Data 2011-12/PAQ_G.xpt")
PhysicalActQ2013 <- read_xpt("Data 2013-14/PAQ_H.xpt")
PhysicalActQ2015 <- read_xpt("Data 2015-16/PAQ_I.xpt")
PhysicalActQ2017 <- read_xpt("Data 2017-18/PAQ_J.xpt")
PhysicalActQ2021 <- read_xpt("Data Aug2021-Aug2022/PAQ_L.xpt")
PhysicalActQP2017 <- read_xpt("Data PP2017-20/P_PAQ.xpt")

PrescriptionMedsQ2011 <- read_xpt("Data 2011-12/RXQ_RX_G.xpt")
PrescriptionMedsQ2013 <- read_xpt("Data 2013-14/RXQ_RX_H.xpt")
PrescriptionMedsQ2015 <- read_xpt("Data 2015-16/RXQ_RX_I.xpt")
PrescriptionMedsQ2017 <- read_xpt("Data 2017-18/RXQ_RX_J.xpt")
PrescriptionMedsQ2021 <- read_xpt("Data Aug2021-Aug2022/RXQ_RX_L.xpt")
PrescriptionMedsQP2017 <- read_xpt("Data PP2017-20/P_RXQ_RX.xpt")

SleepDisordersQ2011 <- read_xpt("Data 2011-12/SLQ_G.xpt")
SleepDisordersQ2013 <- read_xpt("Data 2013-14/SLQ_H.xpt")
SleepDisordersQ2015 <- read_xpt("Data 2015-16/SLQ_I.xpt")
SleepDisordersQ2017 <- read_xpt("Data 2017-18/SLQ_J.xpt")
SleepDisordersQ2021 <- read_xpt("Data Aug2021-Aug2022/SLQ_L.xpt")
SleepDisordersQP2017 <- read_xpt("Data PP2017-20/P_SLQ.xpt")

SmokingQ2011 <- read_xpt("Data 2011-12/SMQ_G.xpt")
SmokingQ2013 <- read_xpt("Data 2013-14/SMQ_H.xpt")
SmokingQ2015 <- read_xpt("Data 2015-16/SMQ_I.xpt")
SmokingQ2017 <- read_xpt("Data 2017-18/SMQ_J.xpt")
SmokingQ2021 <- read_xpt("Data Aug2021-Aug2022/SMQ_L.xpt")
SmokingQP2017 <- read_xpt("Data PP2017-20/P_SMQ.xpt")

WeightHistoryQ2011 <- read_xpt("Data 2011-12/WHQ_G.xpt")
WeightHistoryQ2013 <- read_xpt("Data 2013-14/WHQ_H.xpt")
WeightHistoryQ2015 <- read_xpt("Data 2015-16/WHQ_I.xpt")
WeightHistoryQ2017 <- read_xpt("Data 2017-18/WHQ_J.xpt")
WeightHistoryQ2021 <- read_xpt("Data Aug2021-Aug2022/WHQ_L.xpt")
WeightHistoryQP2017 <- read_xpt("Data PP2017-20/P_WHQ.xpt")

YouthWeightHistoryQ2011 <- read_xpt("Data 2011-12/WHQMEC_G.xpt")
YouthWeightHistoryQ2015 <- read_xpt("Data 2015-16/WHQMEC_I.xpt")
YouthWeightHistoryQ2017 <- read_xpt("Data 2017-18/WHQMEC_J.xpt")
YouthWeightHistoryQP2017 <- read_xpt("Data PP2017-20/P_WHQMEC.xpt")
```

#### Cleaning
```{r}
# Demographics
Demographics2011 <- Demographics2011 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")
Demographics2013 <- Demographics2013 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")
Demographics2015 <- Demographics2015 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")
Demographics2017 <- Demographics2017 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")
Demographics2021 <- Demographics2021 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")
DemographicsPP2017 <- DemographicsPP2017 |>
  select("SEQN", "RIDSTATR", "RIAGENDR","RIDAGEYR", "RIDRETH3", "INDFMPIR")

# Examination
BloodPressure2011 <- BloodPressure2011 |>
  select("SEQN", "PEASCST1", "PEASCTM1", "BPXCHR", "BPQ150A", "BPQ150B", "BPQ150C", "BPQ150D", "BPXPLS", "BPXPULS", "BPXPTY",  "BPXSY1", "BPXSY2", "BPXSY3", "BPXSY4", "BPXDI1", "BPXDI2", "BPXDI3", "BPXDI4")
BloodPressure2013 <- BloodPressure2013 |>
  select("SEQN", "PEASCST1", "PEASCTM1", "BPXCHR", "BPXPLS", "BPXPULS", "BPXPTY",  "BPXSY1", "BPXSY2", "BPXSY3", "BPXSY4", "BPXDI1", "BPXDI2", "BPXDI3", "BPXDI4")
BloodPressure2015 <- BloodPressure2015 |>
  select("SEQN", "BPXCHR", "BPXPULS", "BPXSY1","BPXSY2","BPXSY3", "BPXSY4", "BPXDI1", "BPXDI2", "BPXDI3", "BPXDI4")
BloodPressure2017 <- BloodPressure2017 |>
  select("SEQN", "BPXCHR", "BPXPULS", "BPXSY1","BPXSY2","BPXSY3", "BPXSY4", "BPXDI1", "BPXDI2", "BPXDI3", "BPXDI4")
BloodPressure2021 <- BloodPressure2021 |>
  select("SEQN", "BPXOSY1", "BPXOSY2", "BPXOSY3", "BPXODI1", "BPXODI2",  "BPXODI3", "BPXOPLS1", "BPXOPLS2", "BPXOPLS3")
BloodPressureP2017 <- BloodPressureP2017 |>
  select("SEQN", "BPXOSY1", "BPXOSY2",  "BPXOSY3", "BPXODI1", "BPXODI2", "BPXODI3", "BPXOPLS1", "BPXOPLS2", "BPXOPLS3")

BodyMeasurements2011 <- BodyMeasurements2011 |>
  select("SEQN", "BMXWT",  "BMXBMI",  "BMXHT",  "BMXWAIST", "BMXSAD1", "BMXSAD2", "BMXSAD3", "BMXSAD4")
BodyMeasurements2013 <- BodyMeasurements2013 |>
  select("SEQN","BMXWT",  "BMXBMI",  "BMXHT",  "BMXWAIST", "BMXSAD1", "BMXSAD2", "BMXSAD3", "BMXSAD4")
BodyMeasurements2015 <- BodyMeasurements2015 |>
  select("SEQN","BMXWT",  "BMXBMI",  "BMXHT",  "BMXWAIST", "BMXSAD1", "BMXSAD2", "BMXSAD3", "BMXSAD4")
BodyMeasurements2017 <- BodyMeasurements2017 |>
  select("SEQN","BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
BodyMeasurements2021 <- BodyMeasurements2021 |>
  select("SEQN","BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
BodyMeasurementsP2017 <- BodyMeasurementsP2017 |>
  select("SEQN","BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")

# Lab
TotalChol2011 <- TotalChol2011 |>
  select("SEQN", "LBXTC", "LBDTCSI")
TotalChol2013 <- TotalChol2013 |>
  select("SEQN", "LBXTC", "LBDTCSI")
TotalChol2015 <- TotalChol2015 |>
  select("SEQN", "LBXTC", "LBDTCSI")
TotalChol2017 <- TotalChol2017 |>
  select("SEQN", "LBXTC", "LBDTCSI")
TotalChol2021 <- TotalChol2021 |>
  select("SEQN", "LBXTC", "LBDTCSI","WTPH2YR")
TotalCholP2017 <- TotalCholP2017 |>
  select("SEQN", "LBXTC", "LBDTCSI")

HDL_Chol2011 <- HDL_Chol2011|>
  select("SEQN", "LBDHDD", "LBDHDDSI")
HDL_Chol2013 <- HDL_Chol2013 |>
  select("SEQN", "LBDHDD", "LBDHDDSI")
HDL_Chol2015 <- HDL_Chol2015 |>
  select("SEQN", "LBDHDD", "LBDHDDSI")
HDL_Chol2017 <- HDL_Chol2017 |>
  select("SEQN", "LBDHDD", "LBDHDDSI")
HDL_Chol2021 <- HDL_Chol2021 |>
  select("SEQN","LBDHDD", "LBDHDDSI")
HDL_CholP2017 <- HDL_CholP2017 |>
  select("SEQN", "LBDHDD", "LBDHDDSI")

LDL_Tri_Chol2011 <- LDL_Tri_Chol2011 |>
  select("SEQN", "WTSAF2YR", "LBXTR","LBDTRSI","LBDLDL","LBDLDLSI")
LDL_Tri_Chol2013 <- LDL_Tri_Chol2013 |>
  select("SEQN", "WTSAF2YR" ,"LBXTR","LBDTRSI","LBDLDL","LBDLDLSI")
LDL_Tri_Chol2015 <- LDL_Tri_Chol2015 |>
  select("SEQN", "WTSAF2YR", "LBXTR", "LBDTRSI", "LBDLDL","LBDLDLSI")
LDL_Tri_Chol2017 <- LDL_Tri_Chol2017 |>
  select("SEQN", "WTSAF2YR", "LBXTR", "LBDTRSI", "LBDLDL", "LBDLDLSI", "LBDLDLM", "LBDLDMSI", "LBDLDLN", "LBDLDNSI")
LDL_Tri_Chol2021 <- LDL_Tri_Chol2021 |>
  select("SEQN", "WTSAF2YR","LBXTLG", "LBDTRSI", "LBDLDL", "LBDLDLSI","LBDLDLM","LBDLDMSI","LBDLDLN","LBDLDNSI")
LDL_Tri_CholP2017 <- LDL_Tri_CholP2017 |>
  select("SEQN", "WTSAFPRP", "LBXTR", "LBDTRSI", "LBDLDL","LBDLDLSI","LBDLDLM", "LBDLDMSI","LBDLDLN", "LBDLDNSI")

GLYP2013 <- GLYP2013 |>
  select("SEQN", "WTSSCH2Y","SSGLYP","SSGLYPL")
GLYP2015 <- GLYP2015 |>
  select("SEQN", "WTSSGL2Y","SSGLYP","SSGLYP")
GLYP2017 <- GLYP2017 |>
  select("SEQN", "WTSSBJ2Y", "SSGLYP","SSGLYPL")

Insulin2013 <- Insulin2013 |>
  select("SEQN", "LBXIN", "LBDINSI", "PHAFSTMN")
Insulin2015 <- Insulin2015 |>
  select("SEQN", "LBXIN", "LBDINSI", "PHAFSTMN")
Insulin2017 <- Insulin2017 |>
  select("SEQN", "LBXIN", "LBDINSI")
Insulin2021 <- Insulin2021 |>
  select("SEQN", "LBXIN", "LBDINSI")
InsulinP2017 <- InsulinP2017 |>
  select("SEQN", "LBXIN","LBDINSI","LBDINLC")

#Metals2011 <- Metals2011 |>
#  select("SEQN")
#Metals2013 <- Metals2013 |>
#  select("SEQN")
#Metals2015 <- Metals2015 |>
#  select("SEQN")
#Metals2017 <- Metals2017 |>
#  select("SEQN")
#Metals2021 <- Metals2021 |>
#  select("SEQN")
#MetalsP2017 <- MetalsP2017 |>
#  select("SEQN")

PFAs2011 <- PFAs2011 |>
  select("SEQN", "LBXPFOS", "LBXPFOA", "LBXPFHS","LBXPFNA")
PFAs2013 <- PFAs2013 |>
  select("SEQN", "SSNFOS", "SSMFOS", "SSNFOA", "SSBFOA", "SSPFNA", "SSPFHS")
PFAs2015 <- PFAs2015 |>
  select("SEQN", "LBXNFOS","LBXMFOS", "LBXNFOA","LBXBFOA", "LBXPFHS", "LBXPFNA")
PFAs2017 <- PFAs2017 |>
  select("SEQN", "LBXNFOS", "LBXMFOS", "LBXNFOA", "LBXBFOA", "LBXPFHS", "LBXPFNA")
PFAsP2017 <- PFAsP2017 |>
  select("SEQN", "LBXNFOS", "LBXMFOS", "LBXNFOA", "LBXBFOA", "LBXPFHS", "LBXPFNA")

Hormones2011 <- Hormones2011 |>
  select("SEQN", "LBXTST")
Hormones2013 <- Hormones2013 |>
  select("SEQN", "LBXTST","LBXEST","LBXSHBG")
Hormones2015 <- Hormones2015 |>
  select("SEQN", "LBXTST","LBXEST","LBXSHBG")
Hormones2017 <- Hormones2017 |>
  select("SEQN", "SSTEST", "SSTSHBG", "SSTLUH")
Hormones2021 <- Hormones2021 |>
  select("SEQN", "LBXEST", "LBXSHBG", "LBXLUH" , "LBXTST")
HormonesP2017 <- HormonesP2017 |>
  select("SEQN", "LBXEST", "LBXSHBG", "LBXLUH")

# Questionnaire 
DiabetesQ2011 <- DiabetesQ2011 |>
  select("SEQN", "DIQ010", "DIQ160")
DiabetesQ2013 <- DiabetesQ2013 |>
  select("SEQN", "DIQ010", "DIQ160")
DiabetesQ2015 <- DiabetesQ2015 |>
  select("SEQN", "DIQ010", "DIQ160")
DiabetesQ2017 <- DiabetesQ2017 |>
  select("SEQN", "DIQ010", "DIQ160")
DiabetesQ2021 <- DiabetesQ2021 |>
  select("SEQN", "DIQ010", "DIQ160")
DiabetesQP2017 <- DiabetesQP2017 |>
  select("SEQN", "DIQ010", "DIQ160")

IncomeQ2011 <- IncomeQ2011 |>
  select("SEQN", "INQ020", "INQ012", "INQ030", "INQ060")
IncomeQ2013 <- IncomeQ2013 |>
  select("SEQN", "INQ020", "INQ012", "INQ030", "INQ060")
IncomeQ2015 <- IncomeQ2015 |>
  select("SEQN", "INQ020", "INQ012", "INQ030", "INQ060")
IncomeQ2017 <- IncomeQ2017 |>
  select("SEQN", "INQ020", "INQ012", "INQ030", "INQ060")
IncomeQ2021 <- IncomeQ2021 |>
  select("SEQN", "INDFMMPI", "INDFMMPC")
IncomeQP2017 <- IncomeQP2017 |>
  select("SEQN", "INDFMMPI", "INDFMMPC")

MedicalCondnsQ2011 <- MedicalCondnsQ2011 |>
  select("SEQN", "MCQ010", "MCQ053", "MCQ160A", "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F", "MCQ160G", "MCQ160K", "MCQ160M", "MCQ160L", "MCQ160N", "MCQ220","MCQ230A", "MCQ230B", "MCQ230C", "MCQ230D")
MedicalCondnsQ2013 <- MedicalCondnsQ2013 |>
  select("SEQN", "MCQ010", "AGQ030", "MCQ053", "MCQ070", "MCQ082", "MCQ084", "MCQ084", "MCQ160A", "MCQ160N", "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F", "MCQ160G", "MCQ160M", "MCQ160K", "MCQ170K", "MCQ160L", "MCQ160O", "MCQ203", "MCQ220", "MCQ230A", "MCQ230B", "MCQ230C", "MCQ365A", "MCQ365B", "MCQ365C", "MCQ365D")
MedicalCondnsQ2015 <- MedicalCondnsQ2015 |>
  select("SEQN", "MCQ010", "AGQ030", "MCQ053", "MCQ160A", "MCQ160N", "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F", "MCQ160G", "MCQ160M", "MCQ160K", "MCQ160L", "MCQ160O", "MCQ220", "MCQ230A", "MCQ230B", "MCQ230C", "MCQ230D", "MCQ365A", "MCQ365B", "MCQ365C", "MCQ365D")
MedicalCondnsQ2017 <- MedicalCondnsQ2017 |>
  select("SEQN", "MCQ010", "AGQ030", "MCQ053", "MCQ160A", "MCQ160N", "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F", "MCQ160M", "MCQ160G", "MCQ160K", "MCQ160O", "MCQ160L", "MCQ500", "MCQ550", "MCQ203", "MCQ220", "MCQ230A", "MCQ230B", "MCQ230C","MCQ366A", "MCQ366B", "MCQ366C", "MCQ366D")
MedicalCondnsQ2021 <- MedicalCondnsQ2021 |>
  select("SEQN", "MCQ010", "AGQ030", "MCQ053", "MCQ160A", "MCQ160B", "MCQ160C", "MCQ160D","MCQ160E", "MCQ160F", "MCQ160M", "MCQ160P", "MCQ160L", "MCQ500", "MCQ550", "MCQ220", "MCQ230A", "MCQ230B", "MCQ230C")
MedicalCondnsQP2017 <- MedicalCondnsQP2017 |>
  select("SEQN", "MCQ010", "AGQ030", "MCQ053", "MCQ160A", "MCQ195", "MCQ160B", "MCD180B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F", "MCQ160M", "MCQ160P", "MCQ160L", "MCQ500", "MCQ550", "MCQ220", "MCQ230A", "MCQ230B", "MCQ230C", "MCQ366A", "MCQ366B", "MCQ366C", "MCQ366D")

MentalHealthQ2011 <- MentalHealthQ2011 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")
MentalHealthQ2013 <- MentalHealthQ2013 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")
MentalHealthQ2015 <- MentalHealthQ2015 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")
MentalHealthQ2017 <- MentalHealthQ2017 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")
MentalHealthQ2021 <- MentalHealthQ2021 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")
MentalHealthQP2017 <- MentalHealthQP2017 |>
  select("SEQN", "DPQ010", "DPQ020", "DPQ030", "DPQ040","DPQ050", "DPQ060", "DPQ070", "DPQ080", "DPQ090", "DPQ100")

PestisideQ2011 <- PestisideQ2011 |>
  select("SEQN", "PUQ100", "PUQ110")
PestisideQ2013 <- PestisideQ2013 |>
  select("SEQN", "PUQ100", "PUQ110")
PestisideQ2015 <- PestisideQ2015 |>
  select("SEQN", "PUQ100", "PUQ110")
PestisideQ2017 <- PestisideQ2017 |>
  select("SEQN", "PUQ100", "PUQ110")
PestisideQ2021 <- PestisideQ2021 |>
  select("SEQN", "PUQ100", "PUQ110")
PestisideQP2017 <- PestisideQP2017 |>
  select("SEQN", "PUQ100", "PUQ110")

PhysicalActQ2011 <- PhysicalActQ2011 |>
  select("SEQN", "PAQ706", "PAQ610", "PAQ625", "PAQ650", "PAQ655", "PAQ665", "PAQ670", "PAQ710", "PAQ715")
PhysicalActQ2013 <- PhysicalActQ2013 |>
  select("SEQN", "PAQ610", "PAQ625", "PAQ650", "PAQ655", "PAQ665", "PAQ670", "PAQ710", "PAQ715", "PAQ706")
PhysicalActQ2015 <- PhysicalActQ2015 |>
  select("SEQN", "PAQ610", "PAQ625", "PAQ650", "PAQ655", "PAQ665", "PAQ670", "PAQ710", "PAQ715", "PAQ706")
PhysicalActQ2017 <- PhysicalActQ2017 |>
  select("SEQN", "PAQ610", "PAQ625", "PAQ650", "PAQ655", "PAQ665", "PAQ670")
PhysicalActQ2021 <- PhysicalActQ2021 |>
  select("SEQN", "PAD790Q", "PAD790U", "PAD680")
PhysicalActQP2017 <- PhysicalActQP2017 |>
  select("SEQN", "PAQ610", "PAQ625", "PAQ650", "PAQ655", "PAQ665", "PAQ670")

PrescriptionMedsQ2011 <- PrescriptionMedsQ2011 |>
  select("SEQN", "RXDUSE","RXDDRUG","RXDDRGID","RXQSEEN","RXDDAYS","RXDCOUNT")
PrescriptionMedsQ2013 <- PrescriptionMedsQ2013 |>
  select("SEQN", "RXDUSE","RXDDRUG","RXDDRGID","RXQSEEN","RXDDAYS")
PrescriptionMedsQ2015 <- PrescriptionMedsQ2015 |>
  select("SEQN", "RXDUSE","RXDDRUG","RXDDRGID","RXQSEEN","RXDDAYS","RXDCOUNT")
PrescriptionMedsQ2017 <- PrescriptionMedsQ2017 |>
  select("SEQN", "RXDUSE","RXDDRUG","RXDDRGID","RXQSEEN","RXDDAYS","RXDCOUNT")
PrescriptionMedsQ2021 <- PrescriptionMedsQ2021 |>
  select("SEQN", "RXQ033","RXQ050")
PrescriptionMedsQP2017 <- PrescriptionMedsQP2017 |>
  select("SEQN", "RXDUSE","RXDDRUG","RXDDRGID","RXQSEEN","RXDDAYS","RXDCOUNT")

SleepDisordersQ2011 <- SleepDisordersQ2011 |>
  select("SEQN", "SLD010H", "SLQ050", "SLQ060")
SleepDisordersQ2013 <- SleepDisordersQ2013 |>
  select("SEQN", "SLD010H", "SLQ050", "SLQ060")
SleepDisordersQ2015 <- SleepDisordersQ2015 |>
  select("SEQN", "SLD012", "SLQ040", "SLQ050", "SLQ120", "SLQ030")
SleepDisordersQ2017 <- SleepDisordersQ2017 |>
  select("SEQN", "SLD012", "SLD013","SLQ030","SLQ040","SLQ050","SLQ120")
SleepDisordersQ2021 <- SleepDisordersQ2021 |>
  select("SEQN", "SLD012", "SLQ320", "SLD013")
SleepDisordersQP2017 <- SleepDisordersQP2017 |>
  select("SEQN", "SLD012", "SLQ320", "SLD013", "SLQ030","SLQ040","SLQ050","SLQ120")

SmokingQ2011 <- SmokingQ2011 |>
  select("SEQN", "SMD030", "SMQ040", "SMD650", "SMD100MN", "SMQ020")
SmokingQ2013 <- SmokingQ2013 |>
  select("SEQN", "SMD030", "SMQ040", "SMD650", "SMD100MN", "SMQ020")
SmokingQ2015 <- SmokingQ2015 |>
  select("SEQN", "SMD030", "SMQ040", "SMD650", "SMD100MN", "SMQ020")
SmokingQ2017 <- SmokingQ2017 |>
  select("SEQN", "SMD030", "SMQ040", "SMD650", "SMD100MN", "SMQ020")
SmokingQ2021 <- SmokingQ2021 |>
  select("SEQN", "SMQ040", "SMD650", "SMD100MN", "SMQ020")
SmokingQP2017 <- SmokingQP2017 |>
  select("SEQN", "SMD030", "SMQ040", "SMD650", "SMD100MN", "SMQ020")

WeightHistoryQ2011 <- WeightHistoryQ2011 |>
  select("SEQN", "WHD080E", "WHD080B", "WHD080I", "WHD100R", "WHQ150")
WeightHistoryQ2013 <- WeightHistoryQ2013 |>
  select("SEQN", "WHD080E", "WHD080B", "WHD080I", "WHQ150")
WeightHistoryQ2015 <- WeightHistoryQ2015 |>
  select("SEQN", "WHD080E", "WHD080B", "WHD080I", "WHQ150")
WeightHistoryQ2017 <- WeightHistoryQ2017 |>
  select("SEQN", "WHD080E", "WHD080B", "WHD080I", "WHQ150")
WeightHistoryQ2021 <- WeightHistoryQ2021 |>
  select("SEQN", "WHQ070")
WeightHistoryQP2017 <- WeightHistoryQP2017 |>
  select("SEQN", "WHD080E", "WHD080B", "WHD080I", "WHQ150")
```


#### Merging
```{r}
# Examination
Examination2011 <- BodyMeasurements2011 |>
  full_join(BloodPressure2011, by = c("SEQN" = "SEQN"))

Examination2013 <- BodyMeasurements2013 |>
  full_join(BloodPressure2013, by = c("SEQN" = "SEQN"))

Examination2015 <- BodyMeasurements2015 |>
  full_join(BloodPressure2015, by = c("SEQN" = "SEQN"))

Examination2017 <- BodyMeasurements2017 |>
  full_join(BloodPressure2017, by = c("SEQN" = "SEQN"))

Examination2021 <- BodyMeasurements2021 |>
  full_join(BloodPressure2021, by = c("SEQN" = "SEQN"))

ExaminationP2017 <- BodyMeasurementsP2017 |>
  full_join(BloodPressureP2017, by = c("SEQN" = "SEQN"))

# Lab
Lab2011 <- TotalChol2011 |>
  full_join(HDL_Chol2011, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_Chol2011, by = c("SEQN" = "SEQN")) |>
  full_join(PFAs2011, by = c("SEQN" = "SEQN")) |>
  full_join(Hormones2011, by = c("SEQN" = "SEQN"))

Lab2013 <- TotalChol2013 |>
  full_join(HDL_Chol2013, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_Chol2013, by = c("SEQN" = "SEQN")) |>
  full_join(GLYP2013, by = c("SEQN" = "SEQN")) |>
  full_join(Insulin2013, by = c("SEQN" = "SEQN")) |>
  full_join(PFAs2013, by = c("SEQN" = "SEQN")) |>
  full_join(Hormones2013, by = c("SEQN" = "SEQN"))

Lab2015 <- TotalChol2015 |>
  full_join(HDL_Chol2015, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_Chol2015, by = c("SEQN" = "SEQN")) |>
  full_join(GLYP2015, by = c("SEQN" = "SEQN")) |>
  full_join(Insulin2015, by = c("SEQN" = "SEQN")) |>
  full_join(PFAs2015, by = c("SEQN" = "SEQN")) |>
  full_join(Hormones2015, by = c("SEQN" = "SEQN"))

Lab2017 <- TotalChol2017 |>
  full_join(HDL_Chol2017, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_Chol2017, by = c("SEQN" = "SEQN")) |>
  full_join(GLYP2017, by = c("SEQN" = "SEQN")) |>
  full_join(Insulin2017, by = c("SEQN" = "SEQN")) |>
  full_join(PFAs2017, by = c("SEQN" = "SEQN")) |>
  full_join(Hormones2017, by = c("SEQN" = "SEQN"))

Lab2021 <- TotalChol2021 |>
  full_join(HDL_Chol2021, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_Chol2021, by = c("SEQN" = "SEQN")) |>
  full_join(Insulin2021, by = c("SEQN" = "SEQN")) |>
  full_join(Hormones2021, by = c("SEQN" = "SEQN"))

LabP2017 <- TotalCholP2017 |>
  full_join(HDL_CholP2017, by = c("SEQN" = "SEQN")) |>
  full_join(LDL_Tri_CholP2017, by = c("SEQN" = "SEQN")) |>
  full_join(InsulinP2017, by = c("SEQN" = "SEQN")) |>
  full_join(HormonesP2017, by = c("SEQN" = "SEQN"))

# Questionnaire
Questionnarie2011 <- DiabetesQ2011 |>
  full_join(IncomeQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQ2011, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQ2011, by = c("SEQN" = "SEQN"))

Questionnarie2013 <- DiabetesQ2013 |>
  full_join(IncomeQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQ2013, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQ2013, by = c("SEQN" = "SEQN"))

Questionnarie2015 <- DiabetesQ2015 |>
  full_join(IncomeQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQ2015, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQ2015, by = c("SEQN" = "SEQN"))

Questionnarie2017 <- DiabetesQ2017 |>
  full_join(IncomeQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQ2017, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQ2017, by = c("SEQN" = "SEQN"))

Questionnarie2021 <- DiabetesQ2021 |>
  full_join(IncomeQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQ2021, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQ2021, by = c("SEQN" = "SEQN"))

QuestionnarieP2017 <- DiabetesQP2017 |>
  full_join(IncomeQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(MedicalCondnsQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(MentalHealthQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(PestisideQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(PhysicalActQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(PrescriptionMedsQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(SleepDisordersQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(SmokingQP2017, by = c("SEQN" = "SEQN")) |>
  full_join(WeightHistoryQP2017, by = c("SEQN" = "SEQN"))
```



#### Merge and Export
```{r}
NHANES2011 <- Demographics2011 |>
  full_join(Examination2011, by = c("SEQN" = "SEQN")) |>
  full_join(Lab2011, by = c("SEQN" = "SEQN")) |>
  full_join(Questionnarie2011, by = c("SEQN" = "SEQN"))


NHANES2013 <- Demographics2013 |>
  full_join(Examination2013, by = c("SEQN" = "SEQN")) |>
  full_join(Lab2013, by = c("SEQN" = "SEQN")) |>
  full_join(Questionnarie2013, by = c("SEQN" = "SEQN"))
  
NHANES2015 <- Demographics2015 |>
  full_join(Examination2015, by = c("SEQN" = "SEQN")) |>
  full_join(Lab2015, by = c("SEQN" = "SEQN")) |>
  full_join(Questionnarie2015, by = c("SEQN" = "SEQN"))
  
NHANES2017 <- Demographics2017 |>
  full_join(Examination2017, by = c("SEQN" = "SEQN")) |>
  full_join(Lab2017, by = c("SEQN" = "SEQN")) |>
  full_join(Questionnarie2017, by = c("SEQN" = "SEQN"))
  
NHANES2021 <- Demographics2021 |>
  full_join(Examination2021, by = c("SEQN" = "SEQN")) |>
  full_join(Lab2021, by = c("SEQN" = "SEQN")) |>
  full_join(Questionnarie2021, by = c("SEQN" = "SEQN"))
  
NHANESP2017 <- DemographicsPP2017 |>
  full_join(ExaminationP2017, by = c("SEQN" = "SEQN")) |>
  full_join(LabP2017, by = c("SEQN" = "SEQN")) |>
  full_join(QuestionnarieP2017, by = c("SEQN" = "SEQN"))

write_xpt(NHANES2011, "NHANES2011.xpt")
write_xpt(NHANES2013, "NHANES2013.xpt")
write_xpt(NHANES2015, "NHANES2015.xpt")
write_xpt(NHANES2017, "NHANES2017.xpt")
write_xpt(NHANES2021, "NHANES2021.xpt")
write_xpt(NHANESP2017, "NHANESP2017.xpt")
```


## Distribution Analysis

### Start 2017

```{r}
NHANES2011 <- read_xpt("NHANES2011.xpt")
NHANES2013 <- read_xpt("NHANES2013.xpt") 
NHANES2015 <- read_xpt("NHANES2015.xpt") 
NHANES2017 <- read_xpt("NHANES2017.xpt") 
NHANES2021 <- read_xpt("NHANES2021.xpt") 
NHANESP2017 <- read_xpt("NHANESP2017.xpt") 

sum(dim(NHANES2011), dim(NHANES2013), dim(NHANES2015), dim(NHANES2017), dim(NHANES2021))
## Reminding myself how to do things. :/
PFAsTotal2017 <- NHANES2017 |>
  select("SEQN", "RIDAGEYR", "RIDRETH3", # Individual and age/ethnicity
         "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST",  # Body measurement
         "LBXPFHS", "LBXPFNA", "LBXBFOA", "LBXMFOS", "LBXNFOA", #PFAs
         # Medical Questions
         "MCQ010", "MCQ160G", "MCQ160K", "MCQ160O", # Respiratory & IMMUNE
         "DIQ010", "DIQ160", # METABOLIC
         "MCQ160M", "MCQ160L", "MCQ500", # Endo/Liver
         "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F" # Cardiovascular
         ) |> 
  filter(RIDAGEYR >= 12 & RIDAGEYR <= 75) |>
  mutate(logLBXPFHS = log(LBXPFHS)) |>
  mutate(logLBXPFNA = log(LBXPFNA)) |>
  mutate(logLBXBFOA = log(LBXBFOA)) |>
  mutate(logLBXMFOS = log(LBXMFOS)) |>
  mutate(logLBXNFOA = log(LBXNFOA)) |>
  filter(!is.na(LBXPFHS))

PFAident <- c("SEQN", "RIDAGEYR", "RIDRETH3", "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
PFAlist <- c("LBXPFHS", "LBXPFNA", "LBXBFOA", "LBXMFOS", "LBXNFOA")
PFARespQs <- c("MCQ010", "MCQ160G", "MCQ160K", "MCQ160O")
PFAMetaQs <- c("DIQ010", "DIQ160")
PFAEndoQs <- c("MCQ160M", "MCQ160L", "MCQ500")
PFACardQs <- c("MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F")

PFAsTotal2017Yay <- PFAsTotal2017 |>
  filter(MCQ010 == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsTotal2017Nay <- PFAsTotal2017 |>
  filter(MCQ010 == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsTotal20172 <- PFAsTotal2017 |>
  filter(MCQ010 != 7 & MCQ010 != 9) |>
  mutate(MCQ010 = if_else(MCQ010 == 1, "Yes", "No"))

PFAsEmphysemaYay <- PFAsTotal2017 |>
  filter(MCQ160G == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsEmphysemaNay <- PFAsTotal2017 |>
  filter(MCQ160G == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsEmphysema <- PFAsTotal2017 |>
  filter(MCQ160G != 9) |>
  mutate(MCQ160G = if_else(MCQ160G == 1, "Yes", "No"))

PFAsTotal20173 <- PFAsTotal2017 |>
  mutate(MCQ160L = coalesce(MCQ160L, MCQ500))

```

### MCQ010

```{r}
# Asthma Differences

## FNS
YesAthmaSumm <- summary(PFAsTotal2017Yay)
NoAthmaSumm <- summary(PFAsTotal2017Nay)
YesAthmaSumm
NoAthmaSumm


## PFHS
### ANOVA
AsthmaFitsPFHS <- aov(logLBXPFHS ~ MCQ010, data = PFAsTotal2017)
summary(AsthmaFitsPFHS)

### Mean Difference
diff1 <- diff(tapply(PFAsTotal20172$logLBXPFHS, PFAsTotal20172$MCQ010, mean))
AsthmaDifferencePFHS <- exp(diff1)
AsthmaDifferencePFHS

### Confidence Interval
AsthmaConfIntPFHS <- t.test(logLBXPFHS ~ MCQ010, data = PFAsTotal20172)$conf.int
AsthmaConfIntPFHS

### Plot
ggplot(data = PFAsTotal20172, aes(x = logLBXPFHS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
AsthmaFitsPFNA <- aov(logLBXPFNA ~ MCQ010, data = PFAsTotal2017)
summary(AsthmaFitsPFNA)

### Mean Difference
diff2 <- diff(tapply(PFAsTotal20172$logLBXPFNA, PFAsTotal20172$MCQ010, mean))
AsthmaDifferencePFNA <- exp(diff2)
AsthmaDifferencePFNA

### Confidence Interval
AsthmaConfIntPFNA <- t.test(logLBXPFNA ~ MCQ010, data = PFAsTotal20172)$conf.int
AsthmaConfIntPFNA

### Plot
ggplot(data = PFAsTotal20172, aes(x = logLBXPFNA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
AsthmaFitsBFOA <- aov(logLBXBFOA ~ MCQ010, data = PFAsTotal2017)
summary(AsthmaFitsBFOA)

### Mean Difference
diff3 <- diff(tapply(PFAsTotal20172$logLBXBFOA, PFAsTotal20172$MCQ010, mean))
AsthmaDifferenceBFOA <- exp(diff3)
AsthmaDifferenceBFOA

### Confidence Interval
AsthmaConfIntBFOA <- t.test(logLBXBFOA ~ MCQ010, data = PFAsTotal20172)$conf.int
AsthmaConfIntBFOA

### Plot
ggplot(data = PFAsTotal20172, aes(x = logLBXBFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
AsthmaFitsMFOS <- aov(logLBXMFOS ~ MCQ010, data = PFAsTotal2017)
summary(AsthmaFitsMFOS)

### Mean Difference
diff3 <- diff(tapply(PFAsTotal20172$logLBXMFOS, PFAsTotal20172$MCQ010, mean))
AsthmaDifferenceMFOS <- exp(diff3)
AsthmaDifferenceMFOS

### Confidence Interval
AsthmaConfIntMFOS <- t.test(logLBXMFOS ~ MCQ010, data = PFAsTotal20172)$conf.int
AsthmaConfIntMFOS

### Plot
ggplot(data = PFAsTotal20172, aes(x = logLBXMFOS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
AsthmaFitsNFOA <- aov(logLBXNFOA ~ MCQ010, data = PFAsTotal2017)
summary(AsthmaFitsNFOA)

### Mean Difference
diff3 <- diff(tapply(PFAsTotal20172$logLBXNFOA, PFAsTotal20172$MCQ010, mean))
AsthmaDifferenceNFOA <- exp(diff3)
AsthmaDifferenceNFOA

### Confidence Interval
AsthmaConfIntNFOA <- t.test(logLBXNFOA ~ MCQ010, data = PFAsTotal20172)$conf.int
AsthmaConfIntNFOA

### Plot
ggplot(data = PFAsTotal20172, aes(x = logLBXNFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)
```

### MCQ160G

```{r}
# Emphysema Differences

## FNS
YesEmphySumm <- summary(PFAsEmphysemaYay)
NoEmphySumm <- summary(PFAsEmphysemaNay)
YesEmphySumm
NoEmphySumm


## PFHS
### ANOVA
EmphyFitsPFHS <- aov(logLBXPFHS ~ MCQ160G, data = PFAsTotal2017)
summary(EmphyFitsPFHS)

### Mean Difference
diff1a <- diff(tapply(PFAsEmphysema$logLBXPFHS, PFAsEmphysema$MCQ160G, mean))
EmphyDifferencePFHS <- exp(diff1a)
EmphyDifferencePFHS

### Confidence Interval
EmphyConfIntPFHS <- t.test(logLBXPFHS ~ MCQ160G, data = PFAsEmphysema)$conf.int
EmphyConfIntPFHS

### Plot
ggplot(data = PFAsEmphysema, aes(x = logLBXPFHS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
EmphyFitsPFNA <- aov(logLBXPFNA ~ MCQ160G, data = PFAsTotal2017)
summary(EmphyFitsPFHS)

### Mean Difference
diff1a <- diff(tapply(PFAsEmphysema$logLBXPFNA, PFAsEmphysema$MCQ160G, mean))
EmphyDifferencePFNA <- exp(diff1a)
EmphyDifferencePFNA

### Confidence Interval
EmphyConfIntPFNA <- t.test(logLBXPFNA ~ MCQ160G, data = PFAsEmphysema)$conf.int
EmphyConfIntPFNA

### Plot
ggplot(data = PFAsEmphysema, aes(x = logLBXPFNA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
EmphyFitsBFOA <- aov(logLBXBFOA ~ MCQ160G, data = PFAsTotal2017)
summary(EmphyFitsBFOA)

### Mean Difference
diff1b <- diff(tapply(PFAsEmphysema$logLBXBFOA, PFAsEmphysema$MCQ160G, mean))
EmphyDifferenceBFOA <- exp(diff1b)
EmphyDifferenceBFOA

### Confidence Interval
EmphyConfIntBFOA <- t.test(logLBXBFOA ~ MCQ160G, data = PFAsEmphysema)$conf.int
EmphyConfIntBFOA

### Plot
ggplot(data = PFAsEmphysema, aes(x = logLBXBFOA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
EmphyFitsMFOS <- aov(logLBXMFOS ~ MCQ160G, data = PFAsTotal2017)
summary(EmphyFitsMFOS)

### Mean Difference
diff1c <- diff(tapply(PFAsEmphysema$logLBXMFOS, PFAsEmphysema$MCQ160G, mean))
EmphyDifferenceMFOS <- exp(diff1c)
EmphyDifferenceMFOS

### Confidence Interval
EmphyConfIntMFOS <- t.test(logLBXMFOS ~ MCQ160G, data = PFAsEmphysema)$conf.int
EmphyConfIntMFOS

### Plot
ggplot(data = PFAsEmphysema, aes(x = logLBXMFOS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
EmphyFitsNFOA <- aov(logLBXNFOA ~ MCQ160G, data = PFAsTotal2017)
summary(EmphyFitsNFOA)

### Mean Difference
diff1d <- diff(tapply(PFAsEmphysema$logLBXNFOA, PFAsEmphysema$MCQ160G, mean))
EmphyDifferenceNFOA <- exp(diff1d)
EmphyDifferenceNFOA

### Confidence Interval
EmphyConfIntNFOA <- t.test(logLBXNFOA ~ MCQ160G, data = PFAsEmphysema)$conf.int
EmphyConfIntNFOA

### Plot
ggplot(data = PFAsEmphysema, aes(x = logLBXNFOA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

```

### MCQ160K

```{r}
# Bronchitis Differences

PFAsBronchitisYay <- PFAsTotal2017 |>
  filter(MCQ160K == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsBronchitisNay <- PFAsTotal2017 |>
  filter(MCQ160K == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsBronchitis <- PFAsTotal2017 |>
  filter(MCQ160K != 9) |>
  mutate(MCQ160K = if_else(MCQ160K == 1, "Yes", "No"))

## FNS
YesBronSumm <- summary(PFAsBronchitisYay)
NoBronSumm <- summary(PFAsBronchitisNay)
YesBronSumm
NoBronSumm


## PFHS
### ANOVA
BronFitsPFHS <- aov(logLBXPFHS ~ MCQ160K, data = PFAsTotal2017)
summary(BronFitsPFHS)

### Mean Difference
diff2a <- diff(tapply(PFAsBronchitis$logLBXPFHS, PFAsBronchitis$MCQ160K, mean))
BronDifferencePFHS <- exp(diff2a)
BronDifferencePFHS

### Confidence Interval
BronConfIntPFHS <- t.test(logLBXPFHS ~ MCQ160K, data = PFAsBronchitis)$conf.int
BronConfIntPFHS

### Plot
ggplot(data = PFAsBronchitis, aes(x = logLBXPFHS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
BronFitsPFNA <- aov(logLBXPFNA ~ MCQ160K, data = PFAsTotal2017)
summary(BronFitsPFNA)

### Mean Difference
diff2b <- diff(tapply(PFAsBronchitis$logLBXPFNA, PFAsBronchitis$MCQ160K, mean))
BronDifferencePFNA <- exp(diff2b)
BronDifferencePFNA

### Confidence Interval
BronConfIntPFNA <- t.test(logLBXPFNA ~ MCQ160K, data = PFAsBronchitis)$conf.int
BronConfIntPFNA

### Plot
ggplot(data = PFAsBronchitis, aes(x = logLBXPFNA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
BronFitsBFOA <- aov(logLBXBFOA ~ MCQ160K, data = PFAsTotal2017)
summary(BronFitsBFOA)

### Mean Difference
diff2c <- diff(tapply(PFAsBronchitis$logLBXBFOA, PFAsBronchitis$MCQ160K, mean))
BronDifferenceBFOA <- exp(diff2c)
BronDifferenceBFOA

### Confidence Interval
BronConfIntBFOA <- t.test(logLBXBFOA ~ MCQ160K, data = PFAsBronchitis)$conf.int
BronConfIntBFOA

### Plot
ggplot(data = PFAsBronchitis, aes(x = logLBXBFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
BronFitsMFOS <- aov(logLBXMFOS ~ MCQ160K, data = PFAsTotal2017)
summary(BronFitsMFOS)

### Mean Difference
diff2d <- diff(tapply(PFAsBronchitis$logLBXMFOS, PFAsBronchitis$MCQ160K, mean))
BronDifferenceMFOS <- exp(diff2d)
BronDifferenceMFOS

### Confidence Interval
BronConfIntMFOS <- t.test(logLBXMFOS ~ MCQ160K, data = PFAsBronchitis)$conf.int
BronConfIntMFOS

### Plot
ggplot(data = PFAsBronchitis, aes(x = logLBXMFOS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
BronFitsNFOA <- aov(logLBXNFOA ~ MCQ160K, data = PFAsTotal2017)
summary(BronFitsNFOA)

### Mean Difference
diff2e <- diff(tapply(PFAsBronchitis$logLBXNFOA, PFAsBronchitis$MCQ160K, mean))
BronDifferenceNFOA <- exp(diff2e)
BronDifferenceNFOA

### Confidence Interval
BronConfIntNFOA <- t.test(logLBXNFOA ~ MCQ160K, data = PFAsBronchitis)$conf.int
BronConfIntNFOA

### Plot
ggplot(data = PFAsBronchitis, aes(x = logLBXNFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

```

### MCQ160O - Accidentally labeled as 2011, oopsies

```{r}
# COPD Differences

PFAsCOPDYay2011 <- PFAsTotal2017 |>
  filter(MCQ160O == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsCOPDNay2011 <- PFAsTotal2017 |>
  filter(MCQ160O == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsCOPDTot2011 <- PFAsTotal2017 |>
  filter(MCQ160O != 9 & MCQ160O != 7) |>
  mutate(MCQ160O = if_else(MCQ160O == 1, "Yes", "No"))

## FNS
YesCOPDSumm <- summary(PFAsCOPDYay2011)
NoCOPDSumm <- summary(PFAsCOPDNay2011)
YesCOPDSumm
NoCOPDSumm


## PFHS
### ANOVA
COPDFitsPFHS2011 <- aov(logLBXPFHS ~ MCQ160O, data = PFAsTotal2017)
summary(COPDFitsPFHS2011)

### Mean Difference
diffc11a <- diff(tapply(PFAsCOPDTot2011$logLBXPFHS, PFAsCOPDTot2011$MCQ160O, mean))
COPDDifferencePFHS2011 <- exp(diffc11a)
COPDDifferencePFHS2011

### Confidence Interval
COPDConfIntPFHS2011 <- t.test(logLBXPFHS ~ MCQ160O, data = PFAsCOPDTot2011)$conf.int
COPDConfIntPFHS2011

### Plot
ggplot(data = PFAsCOPDTot2011, aes(x = logLBXPFHS, fill = MCQ160O)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
COPDFitsPFNA2011 <- aov(logLBXPFNA ~ MCQ160O, data = PFAsTotal2017)
summary(COPDFitsPFNA2011)

### Mean Difference
diffc11b <- diff(tapply(PFAsCOPDTot2011$logLBXPFNA, PFAsCOPDTot2011$MCQ160O, mean))
COPDDifferencePFNA2011 <- exp(diffc11b)
COPDDifferencePFNA2011

### Confidence Interval
COPDConfIntPFNA2011 <- t.test(logLBXPFNA ~ MCQ160O, data = PFAsCOPDTot2011)$conf.int
COPDConfIntPFNA2011

### Plot
ggplot(data = PFAsCOPDTot2011, aes(x = logLBXPFNA, fill = MCQ160O)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
COPDFitsBFOA2011 <- aov(logLBXBFOA ~ MCQ160O, data = PFAsTotal2017)
summary(COPDFitsBFOA2011)

### Mean Difference
diffc11c <- diff(tapply(PFAsCOPDTot2011$logLBXBFOA, PFAsCOPDTot2011$MCQ160O, mean))
COPDDifferenceBFOA2011 <- exp(diffc11c)
COPDDifferenceBFOA2011

### Confidence Interval
COPDConfIntBFOA2011 <- t.test(logLBXBFOA ~ MCQ160O, data = PFAsCOPDTot2011)$conf.int
COPDConfIntBFOA2011

### Plot
ggplot(data = PFAsCOPDTot2011, aes(x = logLBXBFOA, fill = MCQ160O)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
COPDFitsMFOS2011 <- aov(logLBXMFOS ~ MCQ160O, data = PFAsTotal2017)
summary(COPDFitsMFOS2011)

### Mean Difference
diffc11d <- diff(tapply(PFAsCOPDTot2011$logLBXMFOS, PFAsCOPDTot2011$MCQ160O, mean))
COPDDifferenceMFOS2011 <- exp(diffc11d)
COPDDifferenceMFOS2011

### Confidence Interval
COPDConfIntMFOS2011 <- t.test(logLBXMFOS ~ MCQ160O, data = PFAsCOPDTot2011)$conf.int
COPDConfIntMFOS2011

### Plot
ggplot(data = PFAsCOPDTot2011, aes(x = logLBXMFOS, fill = MCQ160O)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
COPDFitsNFOA2011 <- aov(logLBXNFOA ~ MCQ160O, data = PFAsTotal2017)
summary(COPDFitsNFOA2011)

### Mean Difference
diffc11e <- diff(tapply(PFAsCOPDTot2011$logLBXNFOA, PFAsCOPDTot2011$MCQ160O, mean))
COPDDifferenceNFOA2011 <- exp(diffc11e)
COPDDifferenceNFOA2011

### Confidence Interval
COPDConfIntNFOA2011 <- t.test(logLBXNFOA ~ MCQ160O, data = PFAsCOPDTot2011)$conf.int
COPDConfIntNFOA2011

### Plot
ggplot(data = PFAsCOPDTot2011, aes(x = logLBXNFOA, fill = MCQ160O)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)
```

### DIQ010

```{r}

```

### DIQ160

```{r}

```

### MCQ160M

```{r}
# Thyroid Differences

PFAsThyroidYay <- PFAsTotal2017 |>
  filter(MCQ160M == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsThyroidNay <- PFAsTotal2017 |>
  filter(MCQ160M == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsThyroid <- PFAsTotal2017 |>
  filter(MCQ160M != c(7, 9)) |>
  mutate(MCQ160M = if_else(MCQ160M == 1, "Yes", "No"))

## FNS
YesThyroidSumm <- summary(PFAsThyroidYay)
NoThyroidSumm <- summary(PFAsThyroidNay)
YesThyroidSumm
NoThyroidSumm


## PFHS
### ANOVA
ThyroidFitsPFHS <- aov(logLBXPFHS ~ MCQ160M, data = PFAsTotal2017)
summary(ThyroidFitsPFHS)

### Mean Difference
diff4a <- diff(tapply(PFAsThyroid$logLBXPFHS, PFAsThyroid$MCQ160M, mean))
ThyroidDifferencePFHS <- exp(diff4a)
ThyroidDifferencePFHS

### Confidence Interval
ThyroidConfIntPFHS <- t.test(logLBXPFHS ~ MCQ160M, data = PFAsThyroid)$conf.int
ThyroidConfIntPFHS

### Plot
ggplot(data = PFAsThyroid, aes(x = logLBXPFHS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
ThyroidFitsPFNA <- aov(logLBXPFNA ~ MCQ160M, data = PFAsTotal2017)
summary(ThyroidFitsPFNA)

### Mean Difference
diff4b <- diff(tapply(PFAsThyroid$logLBXPFNA, PFAsThyroid$MCQ160M, mean))
ThyroidDifferencePFNA <- exp(diff4b)
ThyroidDifferencePFNA

### Confidence Interval
ThyroidConfIntPFNA <- t.test(logLBXPFNA ~ MCQ160M, data = PFAsThyroid)$conf.int
ThyroidConfIntPFNA

### Plot
ggplot(data = PFAsThyroid, aes(x = logLBXPFNA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
ThyroidFitsBFOA <- aov(logLBXBFOA ~ MCQ160M, data = PFAsTotal2017)
summary(ThyroidFitsBFOA)

### Mean Difference
diff4c <- diff(tapply(PFAsThyroid$logLBXBFOA, PFAsThyroid$MCQ160M, mean))
ThyroidDifferenceBFOA <- exp(diff4c)
ThyroidDifferenceBFOA

### Confidence Interval
ThyroidConfIntBFOA <- t.test(logLBXBFOA ~ MCQ160M, data = PFAsThyroid)$conf.int
ThyroidConfIntBFOA

### Plot
ggplot(data = PFAsThyroid, aes(x = logLBXBFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
ThyroidFitsMFOS <- aov(logLBXMFOS ~ MCQ160M, data = PFAsTotal2017)
summary(ThyroidFitsMFOS)

### Mean Difference
diff4d <- diff(tapply(PFAsThyroid$logLBXMFOS, PFAsThyroid$MCQ160M, mean))
ThyroidDifferenceMFOS <- exp(diff4d)
ThyroidDifferenceMFOS

### Confidence Interval
ThyroidConfIntMFOS <- t.test(logLBXMFOS ~ MCQ160M, data = PFAsThyroid)$conf.int
ThyroidConfIntMFOS

### Plot
ggplot(data = PFAsThyroid, aes(x = logLBXMFOS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
ThyroidFitsNFOA <- aov(logLBXNFOA ~ MCQ160M, data = PFAsTotal2017)
summary(ThyroidFitsNFOA)

### Mean Difference
diff4e <- diff(tapply(PFAsThyroid$logLBXNFOA, PFAsThyroid$MCQ160M, mean))
ThyroidDifferenceNFOA <- exp(diff4e)
ThyroidDifferenceNFOA

### Confidence Interval
ThyroidConfIntNFOA <- t.test(logLBXNFOA ~ MCQ160M, data = PFAsThyroid)$conf.int
ThyroidConfIntNFOA

### Plot
ggplot(data = PFAsThyroid, aes(x = logLBXNFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)
```

### MCQ160L Merged with MCQ500

In the case where MCQ160L had an `NA` value, the MCQ500 had a value (and vice-versa). So I merged the two columns so that they would only appear as "MCQ160L", however now it is a fundamentally different variable. So this should only be considered as a general liver disease thing and not on the particular age range that the 160L question is concerned with. :)

```{r}
# Liver Differences

PFAsLiverYay <- PFAsTotal20173 |>
  filter(MCQ160L == 1) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsLiverNay <- PFAsTotal20173 |>
  filter(MCQ160L == 2) |>
  select(-c(PFARespQs, PFAMetaQs, PFAEndoQs, PFACardQs, PFAident))

PFAsLiver <- PFAsTotal20173 |>
  filter(MCQ160L != c(7, 9)) |>
  mutate(MCQ160L = if_else(MCQ160L == 1, "Yes", "No"))

## FNS
YesLiverSumm <- summary(PFAsLiverYay)
NoLiverSumm <- summary(PFAsLiverNay)
YesLiverSumm
NoLiverSumm


## PFHS
### ANOVA
LiverFitsPFHS <- aov(logLBXPFHS ~ MCQ160L, data = PFAsTotal20173)
summary(LiverFitsPFHS)

### Mean Difference
diff5a <- diff(tapply(PFAsLiver$logLBXPFHS, PFAsLiver$MCQ160L, mean))
LiverDifferencePFHS <- exp(diff5a)
LiverDifferencePFHS

### Confidence Interval
LiverConfIntPFHS <- t.test(logLBXPFHS ~ MCQ160L, data = PFAsLiver)$conf.int
LiverConfIntPFHS

### Plot
ggplot(data = PFAsLiver, aes(x = logLBXPFHS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
LiverFitsPFNA <- aov(logLBXPFNA ~ MCQ160L, data = PFAsTotal20173)
summary(LiverFitsPFNA)

### Mean Difference
diff5b <- diff(tapply(PFAsLiver$logLBXPFNA, PFAsLiver$MCQ160L, mean))
LiverDifferencePFNA <- exp(diff5b)
LiverDifferencePFNA

### Confidence Interval
LiverConfIntPFNA <- t.test(logLBXPFNA ~ MCQ160L, data = PFAsLiver)$conf.int
LiverConfIntPFNA

### Plot
ggplot(data = PFAsLiver, aes(x = logLBXPFNA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
LiverFitsBFOA <- aov(logLBXBFOA ~ MCQ160L, data = PFAsTotal20173)
summary(LiverFitsBFOA)

### Mean Difference
diff5c <- diff(tapply(PFAsLiver$logLBXBFOA, PFAsLiver$MCQ160L, mean))
LiverDifferenceBFOA <- exp(diff5c)
LiverDifferenceBFOA

### Confidence Interval
LiverConfIntBFOA <- t.test(logLBXBFOA ~ MCQ160L, data = PFAsLiver)$conf.int
LiverConfIntBFOA

### Plot
ggplot(data = PFAsLiver, aes(x = logLBXBFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
LiverFitsMFOS <- aov(logLBXMFOS ~ MCQ160L, data = PFAsTotal20173)
summary(LiverFitsMFOS)

### Mean Difference
diff5d <- diff(tapply(PFAsLiver$logLBXMFOS, PFAsLiver$MCQ160L, mean))
LiverDifferenceMFOS <- exp(diff5d)
LiverDifferenceMFOS

### Confidence Interval
LiverConfIntMFOS <- t.test(logLBXMFOS ~ MCQ160L, data = PFAsLiver)$conf.int
LiverConfIntMFOS

### Plot
ggplot(data = PFAsLiver, aes(x = logLBXMFOS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
LiverFitsNFOA <- aov(logLBXNFOA ~ MCQ160L, data = PFAsTotal20173)
summary(LiverFitsNFOA)

### Mean Difference
diff5e <- diff(tapply(PFAsLiver$logLBXNFOA, PFAsLiver$MCQ160L, mean))
LiverDifferenceNFOA <- exp(diff5e)
LiverDifferenceNFOA

### Confidence Interval
LiverConfIntNFOA <- t.test(logLBXNFOA ~ MCQ160L, data = PFAsLiver)$conf.int
LiverConfIntNFOA

### Plot
ggplot(data = PFAsLiver, aes(x = logLBXNFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)
```

### MCQ160B

```{r}

```

### MCQ160C

```{r}

```

### MCQ160D

```{r}

```

### MCQ160E

```{r}

```

### MCQ160F

```{r}

```

### Other Years

```{r}
# 2015 Table Building
PFAsTotal2015 <- NHANES2015 |>
  select("SEQN", "RIDAGEYR", "RIDRETH3", # Individual and age/ethnicity
         "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST",  # Body measurement
         "LBXPFHS", "LBXPFNA", "LBXBFOA", "LBXMFOS", "LBXNFOA", #PFAs
         # Medical Questions
         "MCQ010", "MCQ160G", "MCQ160K", "MCQ160O", # Respiratory & IMMUNE
         "DIQ010", "DIQ160", # METABOLIC
         "MCQ160M", "MCQ160L", # Endo/Liver
         "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F" # Cardiovascular
         ) |> 
  filter(RIDAGEYR >= 12 & RIDAGEYR <= 75) |>
  mutate(logLBXPFHS = log(LBXPFHS)) |>
  mutate(logLBXPFNA = log(LBXPFNA)) |>
  mutate(logLBXBFOA = log(LBXBFOA)) |>
  mutate(logLBXMFOS = log(LBXMFOS)) |>
  mutate(logLBXNFOA = log(LBXNFOA)) |>
  filter(!is.na(LBXPFHS))

PFAident2015 <- c("SEQN", "RIDAGEYR", "RIDRETH3", "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
PFAlist2015 <- c("LBXPFHS", "LBXPFNA", "LBXBFOA", "LBXMFOS", "LBXNFOA")
PFARespQs2015 <- c("MCQ010", "MCQ160G", "MCQ160K", "MCQ160O")
PFAMetaQs2015 <- c("DIQ010", "DIQ160")
PFAEndoQs2015 <- c("MCQ160M", "MCQ160L")
PFACardQs2015 <- c("MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F")


# 2013 Table
PFAsTotal2013 <- NHANES2013 |>
  select("SEQN", "RIDAGEYR", "RIDRETH3", # Individual and age/ethnicity
         "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST",  # Body measurement
         "SSPFHS", "SSPFNA", "SSBFOA", "SSMFOS", "SSNFOS", #PFAs
         # Medical Questions
         "MCQ010", "MCQ160G", "MCQ160K", "MCQ160O", # Respiratory & IMMUNE
         "DIQ010", "DIQ160", # METABOLIC
         "MCQ160M", "MCQ160L", # Endo/Liver
         "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F" # Cardiovascular
         ) |> 
  filter(RIDAGEYR >= 12 & RIDAGEYR <= 75) |>
  mutate(logSSPFHS = log(SSPFHS)) |>
  mutate(logSSPFNA = log(SSPFNA)) |>
  mutate(logSSBFOA = log(SSBFOA)) |>
  mutate(logSSMFOS = log(SSMFOS)) |>
  mutate(logSSNFOS = log(SSNFOS)) |>
  filter(!is.na(SSPFHS))

PFAident2013 <- c("SEQN", "RIDAGEYR", "RIDRETH3", "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
PFAlist2013 <- c("SSPFHS", "SSPFNA", "SSBFOA", "SSMFOS", "SSNFOS")
PFARespQs2013 <- c("MCQ010", "MCQ160G", "MCQ160K", "MCQ160O")
PFAMetaQs2013 <- c("DIQ010", "DIQ160")
PFAEndoQs2013 <- c("MCQ160M", "MCQ160L")
PFACardQs2013 <- c("MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F")


# 2011 Table Building
PFAsTotal2011 <- NHANES2011 |>
  select("SEQN", "RIDAGEYR", "RIDRETH3", # Individual and age/ethnicity
         "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST",  # Body measurement
         "LBXPFHS", "LBXPFNA", "LBXPFOA", "LBXPFOS", #PFAs
         # Medical Questions
         "MCQ010", "MCQ160G", "MCQ160K", # Respiratory & IMMUNE
         "DIQ010", "DIQ160", # METABOLIC
         "MCQ160M", "MCQ160L", # Endo/Liver
         "MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F" # Cardiovascular
         ) |> 
  filter(RIDAGEYR >= 12 & RIDAGEYR <= 75) |>
  mutate(logLBXPFHS = log(LBXPFHS)) |>
  mutate(logLBXPFNA = log(LBXPFNA)) |>
  mutate(logLBXPFOA = log(LBXPFOA)) |>
  mutate(logLBXPFOS = log(LBXPFOS)) |>
  filter(!is.na(LBXPFHS))

PFAident2011 <- c("SEQN", "RIDAGEYR", "RIDRETH3", "BMXWT", "BMXHT", "BMXBMI", "BMXWAIST")
PFAlist2011 <- c("LBXPFHS", "LBXPFNA", "LBXPFOA", "LBXPFOS")
PFARespQs2011 <- c("MCQ010", "MCQ160G", "MCQ160K")
PFAMetaQs2011 <- c("DIQ010", "DIQ160")
PFAEndoQs2011 <- c("MCQ160M", "MCQ160L")
PFACardQs2011 <- c("MCQ160B", "MCQ160C", "MCQ160D", "MCQ160E", "MCQ160F")
```

2013 is horrible. I hate 2013, Madi hates 2013, EVERYONE hates 2013. *mic drop*

# Asthma Distributions

```{r}
# 2011 Asthma Analysis

PFAsAsthmaYay2011 <- PFAsTotal2011 |>
  filter(MCQ010 == 1) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsAsthmaNay2011 <- PFAsTotal2011 |>
  filter(MCQ010 == 2) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsAsthmaTot2011 <- PFAsTotal2011 |>
  filter(MCQ010 != 7 & MCQ010 != 9) |>
  mutate(MCQ010 = if_else(MCQ010 == 1, "Yes", "No"))


## FNS
YesAthma2011Summ <- summary(PFAsAsthmaYay2011)
NoAthma2011Summ <- summary(PFAsAsthmaNay2011)
YesAthma2011Summ
NoAthma2011Summ


## PFHS
### ANOVA
AsthmaFits2011PFHS <- aov(logLBXPFHS ~ MCQ010, data = PFAsTotal2011)
summary(AsthmaFits2011PFHS)

### Mean Difference
diff11a <- diff(tapply(PFAsAsthmaTot2011$logLBXPFHS, PFAsAsthmaTot2011$MCQ010, mean))
AsthmaDifference2011PFHS <- exp(diff11a)
AsthmaDifference2011PFHS

### Confidence Interval
AsthmaConfInt2011PFHS <- t.test(logLBXPFHS ~ MCQ010, data = PFAsAsthmaTot2011)$conf.int
AsthmaConfInt2011PFHS

### Plot
ggplot(data = PFAsAsthmaTot2011, aes(x = logLBXPFHS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
AsthmaFits2011PFNA <- aov(logLBXPFNA ~ MCQ010, data = PFAsTotal2011)
summary(AsthmaFits2011PFNA)

### Mean Difference
diff11b <- diff(tapply(PFAsAsthmaTot2011$logLBXPFNA, PFAsAsthmaTot2011$MCQ010, mean))
AsthmaDifference2011PFNA <- exp(diff11b)
AsthmaDifference2011PFNA

### Confidence Interval
AsthmaConfInt2011PFNA <- t.test(logLBXPFNA ~ MCQ010, data = PFAsAsthmaTot2011)$conf.int
AsthmaConfInt2011PFNA

### Plot
ggplot(data = PFAsAsthmaTot2011, aes(x = logLBXPFNA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOA
### ANOVA
AsthmaFits2011PFOA <- aov(logLBXPFOA ~ MCQ010, data = PFAsTotal2011)
summary(AsthmaFits2011PFOA)

### Mean Difference
diff11c <- diff(tapply(PFAsAsthmaTot2011$logLBXPFOA, PFAsAsthmaTot2011$MCQ010, mean))
AsthmaDifference2011PFOA <- exp(diff11c)
AsthmaDifference2011PFOA

### Confidence Interval
AsthmaConfInt2011PFOA <- t.test(logLBXPFOA ~ MCQ010, data = PFAsAsthmaTot2011)$conf.int
AsthmaConfInt2011PFOA

### Plot
ggplot(data = PFAsAsthmaTot2011, aes(x = logLBXPFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOS
### ANOVA
AsthmaFits2011PFOS <- aov(logLBXPFOS ~ MCQ010, data = PFAsTotal2011)
summary(AsthmaFits2011PFOS)

### Mean Difference
diff11d <- diff(tapply(PFAsAsthmaTot2011$logLBXPFOS, PFAsAsthmaTot2011$MCQ010, mean))
AsthmaDifference2011PFOS <- exp(diff11d)
AsthmaDifference2011PFOS

### Confidence Interval
AsthmaConfInt2011PFOS <- t.test(logLBXPFOS ~ MCQ010, data = PFAsAsthmaTot2011)$conf.int
AsthmaConfInt2011PFOS

### Plot
ggplot(data = PFAsAsthmaTot2011, aes(x = logLBXPFOS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

###########################################################################
# 2013 Asthma Analysis

PFAsAsthmaYay2013 <- PFAsTotal2013 |>
  filter(MCQ010 == 1) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsAsthmaNay2013 <- PFAsTotal2013 |>
  filter(MCQ010 == 2) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsAsthmaTot2013 <- PFAsTotal2013 |>
  filter(MCQ010 != 7 & MCQ010 != 9) |>
  mutate(MCQ010 = if_else(MCQ010 == 1, "Yes", "No"))


## FNS
YesAthma2013Summ <- summary(PFAsAsthmaYay2013)
NoAthma2013Summ <- summary(PFAsAsthmaNay2013)
YesAthma2013Summ
NoAthma2013Summ


## PFHS
### ANOVA
AsthmaFits2013PFHS <- aov(logSSPFHS ~ MCQ010, data = PFAsTotal2013)
summary(AsthmaFits2013PFHS)

### Mean Difference
diff13a <- diff(tapply(PFAsAsthmaTot2013$logSSPFHS, PFAsAsthmaTot2013$MCQ010, mean))
AsthmaDifference2013PFHS <- exp(diff13a)
AsthmaDifference2011PFHS

### Confidence Interval
AsthmaConfInt2013PFHS <- t.test(logSSPFHS ~ MCQ010, data = PFAsAsthmaTot2013)$conf.int
AsthmaConfInt2013PFHS

### Plot
ggplot(data = PFAsAsthmaTot2013, aes(x = logSSPFHS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA (SSPFNA)
### ANOVA
AsthmaFits2013PFNA <- aov(logSSPFNA ~ MCQ010, data = PFAsTotal2013)
summary(AsthmaFits2013PFNA)

### Mean Difference
diff13b <- diff(tapply(PFAsAsthmaTot2013$logSSPFNA, PFAsAsthmaTot2013$MCQ010, mean))
AsthmaDifference2013PFNA <- exp(diff13b)
AsthmaDifference2013PFNA

### Confidence Interval
AsthmaConfInt2013PFNA <- t.test(logSSPFNA ~ MCQ010, data = PFAsAsthmaTot2013)$conf.int
AsthmaConfInt2013PFNA

### Plot
ggplot(data = PFAsAsthmaTot2013, aes(x = logSSPFNA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (SSBFOA)
### ANOVA
AsthmaFits2013BFOA <- aov(logSSBFOA ~ MCQ010, data = PFAsTotal2013)
summary(AsthmaFits2013BFOA)

### Mean Difference
diff13c <- diff(tapply(PFAsAsthmaTot2013$logSSBFOA, PFAsAsthmaTot2013$MCQ010, mean))
AsthmaDifference2013BFOA <- exp(diff13c)
AsthmaDifference2013BFOA

### Confidence Interval
AsthmaConfInt2013BFOA <- t.test(logSSBFOA ~ MCQ010, data = PFAsAsthmaTot2013)$conf.int
AsthmaConfInt2013BFOA

### Plot
ggplot(data = PFAsAsthmaTot2013, aes(x = logSSBFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (SSMFOS) & n-PFOA (SSNFOA) are both the same for every individual.
######################################################

# 2015 Asthma Analysis

PFAsAsthmaYay2015 <- PFAsTotal2015 |>
  filter(MCQ010 == 1) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsAsthmaNay2015 <- PFAsTotal2015 |>
  filter(MCQ010 == 2) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsAsthmaTot2015 <- PFAsTotal2015 |>
  filter(MCQ010 != 7 & MCQ010 != 9) |>
  mutate(MCQ010 = if_else(MCQ010 == 1, "Yes", "No"))


## FNS
YesAthma2015Summ <- summary(PFAsAsthmaYay2015)
NoAthma2015Summ <- summary(PFAsAsthmaNay2015)
YesAthma2015Summ
NoAthma2015Summ


## PFHS
### ANOVA
AsthmaFits2015PFHS <- aov(logLBXPFHS ~ MCQ010, data = PFAsTotal2015)
summary(AsthmaFits2015PFHS)

### Mean Difference
diff15a <- diff(tapply(PFAsAsthmaTot2015$logLBXPFHS, PFAsAsthmaTot2015$MCQ010, mean))
AsthmaDifference2015PFHS <- exp(diff15a)
AsthmaDifference2015PFHS

### Confidence Interval
AsthmaConfInt2015PFHS <- t.test(logLBXPFHS ~ MCQ010, data = PFAsAsthmaTot2015)$conf.int
AsthmaConfInt2015PFHS

### Plot
ggplot(data = PFAsAsthmaTot2015, aes(x = logLBXPFHS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
AsthmaFits2015PFNA <- aov(logLBXPFNA ~ MCQ010, data = PFAsTotal2015)
summary(AsthmaFits2015PFNA)

### Mean Difference
diff15b <- diff(tapply(PFAsAsthmaTot2015$logLBXPFNA, PFAsAsthmaTot2015$MCQ010, mean))
AsthmaDifference2015PFNA <- exp(diff15b)
AsthmaDifference2015PFNA

### Confidence Interval
AsthmaConfInt2015PFNA <- t.test(logLBXPFNA ~ MCQ010, data = PFAsAsthmaTot2015)$conf.int
AsthmaConfInt2015PFNA

### Plot
ggplot(data = PFAsAsthmaTot2015, aes(x = logLBXPFNA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
AsthmaFits2015BFOA <- aov(logLBXBFOA ~ MCQ010, data = PFAsTotal2015)
summary(AsthmaFits2015BFOA)

### Mean Difference
diff15c <- diff(tapply(PFAsAsthmaTot2015$logLBXBFOA, PFAsAsthmaTot2015$MCQ010, mean))
AsthmaDifferenceBFOA <- exp(diff15c)
AsthmaDifferenceBFOA

### Confidence Interval
AsthmaConfIntBFOA <- t.test(logLBXBFOA ~ MCQ010, data = PFAsAsthmaTot2015)$conf.int
AsthmaConfIntBFOA

### Plot
ggplot(data = PFAsAsthmaTot2015, aes(x = logLBXBFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
AsthmaFits2015MFOS <- aov(logLBXMFOS ~ MCQ010, data = PFAsTotal2015)
summary(AsthmaFits2015PFNA)

### Mean Difference
diff15d <- diff(tapply(PFAsAsthmaTot2015$logLBXMFOS, PFAsAsthmaTot2015$MCQ010, mean))
AsthmaDifference2015MFOS <- exp(diff15d)
AsthmaDifference2015MFOS

### Confidence Interval
AsthmaConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ010, data = PFAsAsthmaTot2015)$conf.int
AsthmaConfInt2015MFOS

### Plot
ggplot(data = PFAsAsthmaTot2015, aes(x = logLBXMFOS, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
AsthmaFits2015NFOA <- aov(logLBXNFOA ~ MCQ010, data = PFAsTotal2015)
summary(AsthmaFits2015NFOA)

### Mean Difference
diff15e <- diff(tapply(PFAsAsthmaTot2015$logLBXNFOA, PFAsAsthmaTot2015$MCQ010, mean))
AsthmaDifference2015NFOA <- exp(diff15e)
AsthmaDifference2015NFOA

### Confidence Interval
AsthmaConfInt2015NFOA <- t.test(logLBXNFOA ~ MCQ010, data = PFAsAsthmaTot2015)$conf.int
AsthmaConfInt2015NFOA

### Plot
ggplot(data = PFAsAsthmaTot2015, aes(x = logLBXNFOA, fill = MCQ010)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)
```

### Emphysema Distributions

```{r}
# 2011 Emphysema Analysis

PFAsEmphyYay2011 <- PFAsTotal2011 |>
  filter(MCQ160G == 1) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsEmphyNay2011 <- PFAsTotal2011 |>
  filter(MCQ160G == 2) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsEmphyTot2011 <- PFAsTotal2011 |>
  filter(MCQ160G != 7 & MCQ160G != 9) |>
  mutate(MCQ160G = if_else(MCQ160G == 1, "Yes", "No"))


## FNS
YesEmphy2011Summ <- summary(PFAsEmphyYay2011)
NoEmphy2011Summ <- summary(PFAsEmphyNay2011)
YesEmphy2011Summ
NoEmphy2011Summ


## PFHS
### ANOVA
EmphyFits2011PFHS <- aov(logLBXPFHS ~ MCQ160G, data = PFAsTotal2011)
summary(EmphyFits2011PFHS)

### Mean Difference
diffe11a <- diff(tapply(PFAsEmphyTot2011$logLBXPFHS, PFAsEmphyTot2011$MCQ160G, mean))
EmphyDifference2011PFHS <- exp(diffe11a)
EmphyDifference2011PFHS

### Confidence Interval
EmphyConfInt2011PFHS <- t.test(logLBXPFHS ~ MCQ160G, data = PFAsEmphyTot2011)$conf.int
EmphyConfInt2011PFHS

### Plot
ggplot(data = PFAsEmphyTot2011, aes(x = logLBXPFHS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA


########################################################

# 2013 Emphysema Analysis

PFAsEmphyYay2013 <- PFAsTotal2013 |>
  filter(MCQ160G == 1) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsEmphyNay2013 <- PFAsTotal2013 |>
  filter(MCQ160G == 2) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsEmphyTot2013 <- PFAsTotal2013 |>
  filter(MCQ160G != 7 & MCQ160G != 9) |>
  mutate(MCQ160G = if_else(MCQ160G == 1, "Yes", "No"))


## FNS
YesEmphy2013Summ <- summary(PFAsEmphyYay2013)
NoEmphy2013Summ <- summary(PFAsEmphyNay2013)
YesEmphy2013Summ
NoEmphy2013Summ


## PFHS
### ANOVA
EmphyFits2013PFHS <- aov(logSSPFHS ~ MCQ160G, data = PFAsTotal2013)
summary(EmphyFits2013PFHS)

### Mean Difference
diffe13a <- diff(tapply(PFAsEmphyTot2013$logSSPFHS, PFAsEmphyTot2013$MCQ160G, mean))
EmphyDifference2013PFHS <- exp(diffe13a)
EmphyDifference2013PFHS

### Confidence Interval
EmphyConfInt2013PFHS <- t.test(logSSPFHS ~ MCQ160G, data = PFAsEmphyTot2013)$conf.int
AsthmaConfInt2013PFHS

### Plot
ggplot(data = PFAsEmphyTot2013, aes(x = logSSPFHS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA (SSPFNA)
### ANOVA
EmphyFits2013PFNA <- aov(logSSPFNA ~ MCQ160G, data = PFAsTotal2013)
summary(EmphyFits2013PFNA)

### Mean Difference
diffe13b <- diff(tapply(PFAsEmphyTot2013$logSSPFNA, PFAsEmphyTot2013$MCQ160G, mean))
EmphyDifference2013PFNA <- exp(diffe13b)
EmphyDifference2013PFNA

### Confidence Interval
EmphyConfInt2013PFNA <- t.test(logSSPFNA ~ MCQ160G, data = PFAsEmphyTot2013)$conf.int
EmphyConfInt2013PFNA

### Plot
ggplot(data = PFAsEmphyTot2013, aes(x = logSSPFNA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (SSBFOA)
### ANOVA
EmphyFits2013BFOA <- aov(logSSBFOA ~ MCQ160G, data = PFAsTotal2013)
summary(EmphyFits2013BFOA)

### Mean Difference
diffe13c <- diff(tapply(PFAsEmphyTot2013$logSSBFOA, PFAsEmphyTot2013$MCQ160G, mean))
EmphyDifference2013BFOA <- exp(diffe13c)
EmphyDifference2013BFOA

### Confidence Interval
EmphyConfInt2013BFOA <- t.test(logSSBFOA ~ MCQ160G, data = PFAsEmphyTot2013)$conf.int
EmphyConfInt2013BFOA

### Plot
ggplot(data = PFAsEmphyTot2013, aes(x = logSSBFOA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (SSMFOS) & n-PFOA (SSNFOA) are both the same for every individual.

########################################################

# 2015 Emphysema Analysis

PFAsEmphyYay2015 <- PFAsTotal2015 |>
  filter(MCQ160G == 1) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsEmphyNay2015 <- PFAsTotal2015 |>
  filter(MCQ160G == 2) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsEmphyTot2015 <- PFAsTotal2015 |>
  filter(MCQ160G != 7 & MCQ160G != 9) |>
  mutate(MCQ160G = if_else(MCQ160G == 1, "Yes", "No"))


## FNS
YesEmphy2015Summ <- summary(PFAsEmphyYay2015)
NoEmphy2015Summ <- summary(PFAsEmphyNay2015)
YesEmphy2015Summ
NoEmphy2015Summ


## PFHS
### ANOVA
EmphyFits2015PFHS <- aov(logLBXPFHS ~ MCQ160G, data = PFAsTotal2015)
summary(EmphyFits2015PFHS)

### Mean Difference
diffe15a <- diff(tapply(PFAsEmphyTot2015$logLBXPFHS, PFAsEmphyTot2015$MCQ160G, mean))
EmphyDifference2015PFHS <- exp(diffe15a)
EmphyDifference2015PFHS

### Confidence Interval
EmphyConfInt2015PFHS <- t.test(logLBXPFHS ~ MCQ160G, data = PFAsEmphyTot2015)$conf.int
EmphyConfInt2015PFHS

### Plot
ggplot(data = PFAsEmphyTot2015, aes(x = logLBXPFHS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
EmphyFits2015PFNA <- aov(logLBXPFNA ~ MCQ160G, data = PFAsTotal2015)
summary(EmphyFits2015PFNA)

### Mean Difference
diffe15b <- diff(tapply(PFAsEmphyTot2015$logLBXPFNA, PFAsEmphyTot2015$MCQ160G, mean))
EmphyDifference2015PFNA <- exp(diffe15b)
EmphyDifference2015PFNA

### Confidence Interval
EmphyConfInt2015PFNA <- t.test(logLBXPFNA ~ MCQ160G, data = PFAsEmphyTot2015)$conf.int
EmphyConfInt2015PFNA

### Plot
ggplot(data = PFAsEmphyTot2015, aes(x = logLBXPFNA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
EmphyFits2015BFOA <- aov(logLBXBFOA ~ MCQ160G, data = PFAsTotal2015)
summary(EmphyFits2015BFOA)

### Mean Difference
diffe15c <- diff(tapply(PFAsEmphyTot2015$logLBXBFOA, PFAsEmphyTot2015$MCQ160G, mean))
EmphyDifference2015BFOA <- exp(diffe15c)
EmphyDifference2015BFOA

### Confidence Interval
EmphyConfInt2015BFOA <- t.test(logLBXBFOA ~ MCQ160G, data = PFAsEmphyTot2015)$conf.int
EmphyConfInt2015BFOA

### Plot
ggplot(data = PFAsEmphyTot2015, aes(x = logLBXBFOA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
EmphyFits2015MFOS <- aov(logLBXMFOS ~ MCQ160G, data = PFAsTotal2015)
summary(EmphyFits2015MFOS)

### Mean Difference
diffe15d <- diff(tapply(PFAsEmphyTot2015$logLBXMFOS, PFAsEmphyTot2015$MCQ160G, mean))
EmphyDifference2015MFOS <- exp(diffe15d)
EmphyDifference2015MFOS

### Confidence Interval
EmphyConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ160G, data = PFAsEmphyTot2015)$conf.int
EmphyConfInt2015MFOS

### Plot
ggplot(data = PFAsEmphyTot2015, aes(x = logLBXMFOS, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
EmphyFits2015NFOA <- aov(logLBXNFOA ~ MCQ160G, data = PFAsTotal2015)
summary(EmphyFits2015NFOA)

### Mean Difference
diffe15e <- diff(tapply(PFAsEmphyTot2015$logLBXNFOA, PFAsEmphyTot2015$MCQ160G, mean))
EmphyDifference2015NFOA <- exp(diffe15e)
EmphyDifference2015NFOA

### Confidence Interval
EmphyConfInt2015NFOA <- t.test(logLBXNFOA ~ MCQ160G, data = PFAsEmphyTot2015)$conf.int
EmphyConfInt2015NFOA

### Plot
ggplot(data = PFAsEmphyTot2015, aes(x = logLBXNFOA, fill = MCQ160G)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

```

### Bronchitis Distributions

```{r}
# 2011 Bronchitis Analysis

PFAsBronYay2011 <- PFAsTotal2011 |>
  filter(MCQ160K == 1) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsBronNay2011 <- PFAsTotal2011 |>
  filter(MCQ160K == 2) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsBronTot2011 <- PFAsTotal2011 |>
  filter(MCQ160K != 7 & MCQ160K != 9) |>
  mutate(MCQ160K = if_else(MCQ160K == 1, "Yes", "No"))


## FNS
YesBron2011Summ <- summary(PFAsBronYay2011)
NoBron2011Summ <- summary(PFAsBronNay2011)
YesBron2011Summ
NoBron2011Summ


## PFHS
### ANOVA
BronFits2011PFHS <- aov(logLBXPFHS ~ MCQ160K, data = PFAsTotal2011)
summary(BronFits2011PFHS)

### Mean Difference
diffb11a <- diff(tapply(PFAsBronTot2011$logLBXPFHS, PFAsBronTot2011$MCQ160K, mean))
BronDifference2011PFHS <- exp(diffb11a)
BronDifference2011PFHS

### Confidence Interval
BronConfInt2011PFHS <- t.test(logLBXPFHS ~ MCQ160K, data = PFAsBronTot2011)$conf.int
BronConfInt2011PFHS

### Plot
ggplot(data = PFAsBronTot2011, aes(x = logLBXPFHS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
BronFits2011PFNA <- aov(logLBXPFNA ~ MCQ160K, data = PFAsTotal2011)
summary(BronFits2011PFNA)

### Mean Difference
diffb11b <- diff(tapply(PFAsBronTot2011$logLBXPFNA, PFAsBronTot2011$MCQ160K, mean))
BronDifference2011PFNA <- exp(diffb11b)
BronDifference2011PFNA

### Confidence Interval
BronConfInt2011PFNA <- t.test(logLBXPFNA ~ MCQ160K, data = PFAsBronTot2011)$conf.int
BronConfInt2011PFNA

### Plot
ggplot(data = PFAsBronTot2011, aes(x = logLBXPFNA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
BronFits2011BFOA <- aov(logLBXBFOA ~ MCQ160K, data = PFAsTotal2011)
summary(BronFits2015BFOA)

### Mean Difference
diffb15c <- diff(tapply(PFAsBronTot2011$logLBXBFOA, PFAsBronTot2011$MCQ160K, mean))
BronDifference2015BFOA <- exp(diffb15c)
BronDifference2015BFOA

### Confidence Interval
BronConfInt2015BFOA <- t.test(logLBXBFOA ~ MCQ160K, data = PFAsBronTot2011)$conf.int
BronConfInt2015BFOA

### Plot
ggplot(data = PFAsBronTot2011, aes(x = logLBXBFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
BronFits2015MFOS <- aov(logLBXMFOS ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015MFOS)

### Mean Difference
diffb15d <- diff(tapply(PFAsBronTot2011$logLBXMFOS, PFAsBronTot2011$MCQ160K, mean))
BronDifference2015MFOS <- exp(diffb15d)
BronDifference2015MFOS

### Confidence Interval
BronConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ160K, data = PFAsBronTot2011)$conf.int
BronConfInt2015MFOS

### Plot
ggplot(data = PFAsBronTot2011, aes(x = logLBXMFOS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
BronFits2015NFOA <- aov(logLBXNFOA ~ MCQ160K, data = PFAsTotal2011)
summary(BronFits2015NFOA)

### Mean Difference
diffb15e <- diff(tapply(PFAsBronTot2011$logLBXNFOA, PFAsBronTot2011$MCQ160K, mean))
BronDifference2015NFOA <- exp(diffb15e)
BronDifference2015NFOA

### Confidence Interval
BronConfInt2011NFOA <- t.test(logLBXNFOA ~ MCQ160K, data = PFAsBronTot2011)$conf.int
BronConfInt2015NFOA

### Plot
ggplot(data = PFAsBronTot2011, aes(x = logLBXNFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

#####################################################

# 2013 Bronchitis Analysis

PFAsBronYay2013 <- PFAsTotal2013 |>
  filter(MCQ160K == 1) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsBronNay2013 <- PFAsTotal2013 |>
  filter(MCQ160K == 2) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsBronTot2013 <- PFAsTotal2013 |>
  filter(MCQ160K != 7 & MCQ160K != 9) |>
  mutate(MCQ160K = if_else(MCQ160K == 1, "Yes", "No"))


## FNS
YesBron2013Summ <- summary(PFAsBronYay2013)
NoBron2013Summ <- summary(PFAsBronNay2013)
YesBron2013Summ
NoBron2013Summ


## PFHS
### ANOVA
BronFits2013PFHS <- aov(logSSPFHS ~ MCQ160K, data = PFAsTotal2013)
summary(BronFits2013PFHS)

### Mean Difference
diffb13a <- diff(tapply(PFAsBronTot2013$logSSPFHS, PFAsBronTot2013$MCQ160K, mean))
BronDifference2013PFHS <- exp(diffb13a)
BronDifference2013PFHS

### Confidence Interval
BronConfInt2013PFHS <- t.test(logSSPFHS ~ MCQ160K, data = PFAsBronTot2013)$conf.int
BronConfInt2013PFHS

### Plot
ggplot(data = PFAsBronTot2013, aes(x = logSSPFHS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA (SSPFNA)
### ANOVA
BronFits2013PFNA <- aov(logSSPFNA ~ MCQ160K, data = PFAsTotal2013)
summary(BronFits2013PFNA)

### Mean Difference
diffb13b <- diff(tapply(PFAsBronTot2013$logSSPFNA, PFAsBronTot2013$MCQ160K, mean))
BronDifference2013PFNA <- exp(diffb13b)
BronDifference2013PFNA

### Confidence Interval
BronConfInt2013PFNA <- t.test(logSSPFNA ~ MCQ160K, data = PFAsBronTot2013)$conf.int
BronConfInt2013PFNA

### Plot
ggplot(data = PFAsBronTot2013, aes(x = logSSPFNA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (SSBFOA)
### ANOVA
BronFits2013BFOA <- aov(logSSBFOA ~ MCQ160K, data = PFAsTotal2013)
summary(BronFits2013BFOA)

### Mean Difference
diffb13c <- diff(tapply(PFAsBronTot2013$logSSBFOA, PFAsBronTot2013$MCQ160K, mean))
BronDifference2013BFOA <- exp(diffb13c)
BronDifference2013BFOA

### Confidence Interval
BronConfInt2013BFOA <- t.test(logSSBFOA ~ MCQ160K, data = PFAsBronTot2013)$conf.int
BronConfInt2013BFOA

### Plot
ggplot(data = PFAsBronTot2013, aes(x = logSSBFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (SSMFOS) & n-PFOA (SSNFOA) are both the same for every individual.

#####################################################

# 2015 Bronchitis Analysis

PFAsBronYay2015 <- PFAsTotal2015 |>
  filter(MCQ160K == 1) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsBronNay2015 <- PFAsTotal2015 |>
  filter(MCQ160K == 2) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsBronTot2015 <- PFAsTotal2015 |>
  filter(MCQ160K != 7 & MCQ160K != 9) |>
  mutate(MCQ160K = if_else(MCQ160K == 1, "Yes", "No"))


## FNS
YesBron2015Summ <- summary(PFAsBronYay2015)
NoBron2015Summ <- summary(PFAsBronNay2015)
YesBron2015Summ
NoBron2015Summ


## PFHS
### ANOVA
BronFits2015PFHS <- aov(logLBXPFHS ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015PFHS)

### Mean Difference
diffb15a <- diff(tapply(PFAsBronTot2015$logLBXPFHS, PFAsBronTot2015$MCQ160K, mean))
BronDifference2015PFHS <- exp(diffb15a)
BronDifference2015PFHS

### Confidence Interval
BronConfInt2015PFHS <- t.test(logLBXPFHS ~ MCQ160K, data = PFAsBronTot2015)$conf.int
BronConfInt2015PFHS

### Plot
ggplot(data = PFAsBronTot2015, aes(x = logLBXPFHS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
BronFits2015PFNA <- aov(logLBXPFNA ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015PFNA)

### Mean Difference
diffb15b <- diff(tapply(PFAsBronTot2015$logLBXPFNA, PFAsBronTot2015$MCQ160K, mean))
BronDifference2015PFNA <- exp(diffb15b)
BronDifference2015PFNA

### Confidence Interval
BronConfInt2015PFNA <- t.test(logLBXPFNA ~ MCQ160K, data = PFAsBronTot2015)$conf.int
BronConfInt2015PFNA

### Plot
ggplot(data = PFAsBronTot2015, aes(x = logLBXPFNA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
BronFits2015BFOA <- aov(logLBXBFOA ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015BFOA)

### Mean Difference
diffb15c <- diff(tapply(PFAsBronTot2015$logLBXBFOA, PFAsBronTot2015$MCQ160K, mean))
BronDifference2015BFOA <- exp(diffb15c)
BronDifference2015BFOA

### Confidence Interval
BronConfInt2015BFOA <- t.test(logLBXBFOA ~ MCQ160K, data = PFAsBronTot2015)$conf.int
BronConfInt2015BFOA

### Plot
ggplot(data = PFAsBronTot2015, aes(x = logLBXBFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
BronFits2015MFOS <- aov(logLBXMFOS ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015MFOS)

### Mean Difference
diffb15d <- diff(tapply(PFAsBronTot2015$logLBXMFOS, PFAsBronTot2015$MCQ160K, mean))
BronDifference2015MFOS <- exp(diffb15d)
BronDifference2015MFOS

### Confidence Interval
BronConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ160K, data = PFAsBronTot2015)$conf.int
BronConfInt2015MFOS

### Plot
ggplot(data = PFAsBronTot2015, aes(x = logLBXMFOS, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
BronFits2015NFOA <- aov(logLBXNFOA ~ MCQ160K, data = PFAsTotal2015)
summary(BronFits2015NFOA)

### Mean Difference
diffb15e <- diff(tapply(PFAsBronTot2015$logLBXNFOA, PFAsBronTot2015$MCQ160K, mean))
BronDifference2015NFOA <- exp(diffb15e)
BronDifference2015NFOA

### Confidence Interval
BronConfInt2015NFOA <- t.test(logLBXNFOA ~ MCQ160K, data = PFAsBronTot2015)$conf.int
BronConfInt2015NFOA

### Plot
ggplot(data = PFAsBronTot2015, aes(x = logLBXNFOA, fill = MCQ160K)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

```

### Thyroid Distributions

```{r}
# 2011 Thyroid Analysis

PFAsThyroidYay2011 <- PFAsTotal2011 |>
  filter(MCQ160M == 1) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsThyroidNay2011 <- PFAsTotal2011 |>
  filter(MCQ160M == 2) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsThyroidTot2011 <- PFAsTotal2011 |>
  filter(MCQ160M != 7 & MCQ160M != 9) |>
  mutate(MCQ160M = if_else(MCQ160M == 1, "Yes", "No"))


## FNS
YesThyroid2011Summ <- summary(PFAsThyroidYay2011)
NoThyroid2011Summ <- summary(PFAsThyroidNay2011)
YesThyroid2011Summ
NoThyroid2011Summ


## PFHS
### ANOVA
ThyroidFits2011PFHS <- aov(logLBXPFHS ~ MCQ160M, data = PFAsTotal2011)
summary(ThyroidFits2011PFHS)

### Mean Difference
difft11a <- diff(tapply(PFAsThyroidTot2011$logLBXPFHS, PFAsThyroidTot2011$MCQ160M, mean))
ThyroidDifference2011PFHS <- exp(difft11a)
ThyroidDifference2011PFHS

### Confidence Interval
ThyroidConfInt2011PFHS <- t.test(logLBXPFHS ~ MCQ160M, data = PFAsThyroidTot2011)$conf.int
ThyroidConfInt2011PFHS

### Plot
ggplot(data = PFAsThyroidTot2011, aes(x = logLBXPFHS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
ThyroidFits2011PFNA <- aov(logLBXPFNA ~ MCQ160M, data = PFAsTotal2011)
summary(ThyroidFits2011PFNA)

### Mean Difference
difft11b <- diff(tapply(PFAsThyroidTot2011$logLBXPFNA, PFAsThyroidTot2011$MCQ160M, mean))
ThyroidDifference2011PFNA <- exp(difft11b)
ThyroidDifference2011PFNA

### Confidence Interval
ThyroidConfInt2011PFNA <- t.test(logLBXPFNA ~ MCQ160M, data = PFAsThyroidTot2011)$conf.int
ThyroidConfInt2011PFNA

### Plot
ggplot(data = PFAsThyroidTot2011, aes(x = logLBXPFNA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOA
### ANOVA
ThyroidFits2011PFOA <- aov(logLBXPFOA ~ MCQ160M, data = PFAsTotal2011)
summary(ThyroidFits2011PFOA)

### Mean Difference
difft11c <- diff(tapply(PFAsThyroidTot2011$logLBXPFOA, PFAsThyroidTot2011$MCQ160M, mean))
ThyroidDifference2011PFOA <- exp(difft11c)
ThyroidDifference2011PFOA

### Confidence Interval
ThyroidConfInt2011PFOA <- t.test(logLBXPFOA ~ MCQ160M, data = PFAsThyroidTot2011)$conf.int
ThyroidConfInt2011PFOA

### Plot
ggplot(data = PFAsThyroidTot2011, aes(x = logLBXPFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOS
### ANOVA
ThyroidFits2011PFOS <- aov(logLBXPFOS ~ MCQ160M, data = PFAsTotal2011)
summary(ThyroidFits2011PFOS)

### Mean Difference
difft11d <- diff(tapply(PFAsThyroidTot2011$logLBXPFOS, PFAsThyroidTot2011$MCQ160M, mean))
ThyroidDifference2011PFOS <- exp(difft11d)
ThyroidDifference2011PFOS

### Confidence Interval
ThyroidConfInt2011PFOS <- t.test(logLBXPFOS ~ MCQ160M, data = PFAsThyroidTot2011)$conf.int
ThyroidConfInt2011PFOS

### Plot
ggplot(data = PFAsThyroidTot2011, aes(x = logLBXPFOS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


##################################################

# 2013 Thyroid Analysis

PFAsThyroidYay2013 <- PFAsTotal2013 |>
  filter(MCQ160M == 1) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsThyroidNay2013 <- PFAsTotal2013 |>
  filter(MCQ160M == 2) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsThyroidTot2013 <- PFAsTotal2013 |>
  filter(MCQ160M != 7 & MCQ160M != 9) |>
  mutate(MCQ160M = if_else(MCQ160M == 1, "Yes", "No"))


## FNS
YesThyroid2013Summ <- summary(PFAsThyroidYay2013)
NoThyroid2013Summ <- summary(PFAsThyroidNay2013)
YesThyroid2013Summ
NoThyroid2013Summ


## PFHS
### ANOVA
ThyroidFits2013PFHS <- aov(logSSPFHS ~ MCQ160M, data = PFAsTotal2013)
summary(ThyroidFits2013PFHS)

### Mean Difference
difft13a <- diff(tapply(PFAsThyroidTot2013$logSSPFHS, PFAsThyroidTot2013$MCQ160M, mean))
ThyroidDifference2013PFHS <- exp(difft13a)
ThyroidDifference2013PFHS

### Confidence Interval
ThyroidConfInt2013PFHS <- t.test(logSSPFHS ~ MCQ160M, data = PFAsThyroidTot2013)$conf.int
ThyroidConfInt2013PFHS

### Plot
ggplot(data = PFAsThyroidTot2013, aes(x = logSSPFHS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA (SSPFNA)
### ANOVA
ThyroidFits2013PFNA <- aov(logSSPFNA ~ MCQ160M, data = PFAsTotal2013)
summary(ThyroidFits2013PFNA)

### Mean Difference
difft13b <- diff(tapply(PFAsThyroidTot2013$logSSPFNA, PFAsThyroidTot2013$MCQ160M, mean))
ThyroidDifference2013PFNA <- exp(difft13b)
ThyroidDifference2013PFNA

### Confidence Interval
ThyroidConfInt2013PFNA <- t.test(logSSPFNA ~ MCQ160M, data = PFAsThyroidTot2013)$conf.int
ThyroidConfInt2013PFNA

### Plot
ggplot(data = PFAsThyroidTot2013, aes(x = logSSPFNA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (SSBFOA)
### ANOVA
ThyroidFits2013BFOA <- aov(logSSBFOA ~ MCQ160M, data = PFAsTotal2013)
summary(ThyroidFits2013BFOA)

### Mean Difference
difft13c <- diff(tapply(PFAsThyroidTot2013$logSSBFOA, PFAsThyroidTot2013$MCQ160M, mean))
ThyroidDifference2013BFOA <- exp(difft13c)
ThyroidDifference2013BFOA

### Confidence Interval
ThyroidConfInt2013BFOA <- t.test(logSSBFOA ~ MCQ160M, data = PFAsThyroidTot2013)$conf.int
ThyroidConfInt2013BFOA

### Plot
ggplot(data = PFAsThyroidTot2013, aes(x = logSSBFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (SSMFOS) & n-PFOA (SSNFOA) are both the same for every individual.

##################################################

# 2015 Thyroid Analysis

PFAsThyroidYay2015 <- PFAsTotal2015 |>
  filter(MCQ160M == 1) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsThyroidNay2015 <- PFAsTotal2015 |>
  filter(MCQ160M == 2) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsThyroidTot2015 <- PFAsTotal2015 |>
  filter(MCQ160M != 7 & MCQ160M != 9) |>
  mutate(MCQ160M = if_else(MCQ160M == 1, "Yes", "No"))


## FNS
YesThyroid2015Summ <- summary(PFAsThyroidYay2015)
NoThyroid2015Summ <- summary(PFAsThyroidNay2015)
YesThyroid2015Summ
NoThyroid2015Summ


## PFHS
### ANOVA
ThyroidFits2015PFHS <- aov(logLBXPFHS ~ MCQ160M, data = PFAsTotal2015)
summary(ThyroidFits2015PFHS)

### Mean Difference
difft15a <- diff(tapply(PFAsThyroidTot2015$logLBXPFHS, PFAsThyroidTot2015$MCQ160M, mean))
ThyroidDifference2015PFHS <- exp(difft15a)
ThyroidDifference2015PFHS

### Confidence Interval
ThyroidConfInt2015PFHS <- t.test(logLBXPFHS ~ MCQ160M, data = PFAsThyroidTot2015)$conf.int
ThyroidConfInt2015PFHS

### Plot
ggplot(data = PFAsThyroidTot2015, aes(x = logLBXPFHS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
ThyroidFits2015PFNA <- aov(logLBXPFNA ~ MCQ160M, data = PFAsTotal2015)
summary(ThyroidFits2015PFNA)

### Mean Difference
difft15b <- diff(tapply(PFAsThyroidTot2015$logLBXPFNA, PFAsThyroidTot2015$MCQ160M, mean))
ThyroidDifference2015PFNA <- exp(difft15b)
ThyroidDifference2015PFNA

### Confidence Interval
ThyroidConfInt2015PFNA <- t.test(logLBXPFNA ~ MCQ160M, data = PFAsThyroidTot2015)$conf.int
ThyroidConfInt2015PFNA

### Plot
ggplot(data = PFAsThyroidTot2015, aes(x = logLBXPFNA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
ThyroidFits2015BFOA <- aov(logLBXBFOA ~ MCQ160M, data = PFAsTotal2015)
summary(ThyroidFits2015BFOA)

### Mean Difference
difft15c <- diff(tapply(PFAsThyroidTot2015$logLBXBFOA, PFAsThyroidTot2015$MCQ160M, mean))
ThyroidDifference2015BFOA <- exp(difft15c)
ThyroidDifference2015BFOA

### Confidence Interval
ThyroidConfInt2015BFOA <- t.test(logLBXBFOA ~ MCQ160M, data = PFAsThyroidTot2015)$conf.int
ThyroidConfInt2015BFOA

### Plot
ggplot(data = PFAsThyroidTot2015, aes(x = logLBXBFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
ThyroidFits2015MFOS <- aov(logLBXMFOS ~ MCQ160M, data = PFAsTotal2015)
summary(ThyroidFits2015MFOS)

### Mean Difference
difft15d <- diff(tapply(PFAsThyroidTot2015$logLBXMFOS, PFAsThyroidTot2015$MCQ160M, mean))
ThyroidDifference2015MFOS <- exp(difft15d)
ThyroidDifference2015MFOS

### Confidence Interval
ThyroidConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ160M, data = PFAsThyroidTot2015)$conf.int
ThyroidConfInt2015MFOS

### Plot
ggplot(data = PFAsThyroidTot2015, aes(x = logLBXMFOS, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
ThyroidFits2015NFOA <- aov(logLBXNFOA ~ MCQ160M, data = PFAsTotal2015)
summary(ThyroidFits2015NFOA)

### Mean Difference
difft15e <- diff(tapply(PFAsThyroidTot2015$logLBXNFOA, PFAsThyroidTot2015$MCQ160M, mean))
ThyroidDifference2015NFOA <- exp(difft15e)
ThyroidDifference2015NFOA

### Confidence Interval
ThyroidConfInt2015NFOA <- t.test(logLBXNFOA ~ MCQ160M, data = PFAsThyroidTot2015)$conf.int
ThyroidConfInt2015NFOA

### Plot
ggplot(data = PFAsThyroidTot2015, aes(x = logLBXNFOA, fill = MCQ160M)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


```

### Liver Distributions

```{r}
# 2011 Liver Analysis

PFAsLiverYay2011 <- PFAsTotal2011 |>
  filter(MCQ160L == 1) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsLiverNay2011 <- PFAsTotal2011 |>
  filter(MCQ160L == 2) |>
  select(-c(PFARespQs2011, PFAMetaQs2011, PFAEndoQs2011, PFACardQs2011, PFAident2011))

PFAsLiverTot2011 <- PFAsTotal2011 |>
  filter(MCQ160L != 7 & MCQ160L != 9) |>
  mutate(MCQ160L = if_else(MCQ160L == 1, "Yes", "No"))


## FNS
YesLiver2011Summ <- summary(PFAsLiverYay2011)
NoLiver2011Summ <- summary(PFAsLiverNay2011)
YesLiver2011Summ
NoLiver2011Summ


## PFHS
### ANOVA
LiverFits2011PFHS <- aov(logLBXPFHS ~ MCQ160L, data = PFAsTotal2011)
summary(ThyroidFits2011PFHS)

### Mean Difference
diffl11a <- diff(tapply(PFAsLiverTot2011$logLBXPFHS, PFAsLiverTot2011$MCQ160L, mean))
LiverDifference2011PFHS <- exp(diffl11a)
ThyroidDifference2011PFHS

### Confidence Interval
LiverConfInt2011PFHS <- t.test(logLBXPFHS ~ MCQ160L, data = PFAsLiverTot2011)$conf.int
ThyroidConfInt2011PFHS

### Plot
ggplot(data = PFAsLiverTot2011, aes(x = logLBXPFHS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
LiverFits2011PFNA <- aov(logLBXPFNA ~ MCQ160L, data = PFAsTotal2011)
summary(ThyroidFits2011PFNA)

### Mean Difference
diffl11b <- diff(tapply(PFAsLiverTot2011$logLBXPFNA, PFAsLiverTot2011$MCQ160L, mean))
LiverDifference2011PFNA <- exp(diffl11b)
ThyroidDifference2011PFNA

### Confidence Interval
LiverConfInt2011PFNA <- t.test(logLBXPFNA ~ MCQ160L, data = PFAsLiverTot2011)$conf.int
ThyroidConfInt2011PFNA

### Plot
ggplot(data = PFAsLiverTot2011, aes(x = logLBXPFNA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOA
### ANOVA
LiverFits2011PFOA <- aov(logLBXPFOA ~ MCQ160L, data = PFAsTotal2011)
summary(ThyroidFits2011PFOA)

### Mean Difference
diffl11c <- diff(tapply(PFAsLiverTot2011$logLBXPFOA, PFAsLiverTot2011$MCQ160L, mean))
LiverDifference2011PFOA <- exp(diffl11c)
ThyroidDifference2011PFOA

### Confidence Interval
LiverConfInt2011PFOA <- t.test(logLBXPFOA ~ MCQ160L, data = PFAsLiverTot2011)$conf.int
ThyroidConfInt2011PFOA

### Plot
ggplot(data = PFAsLiverTot2011, aes(x = logLBXPFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFOS
### ANOVA
LiverFits2011PFOS <- aov(logLBXPFOS ~ MCQ160L, data = PFAsTotal2011)
summary(ThyroidFits2011PFOS)

### Mean Difference
diffl11d <- diff(tapply(PFAsLiverTot2011$logLBXPFOS, PFAsLiverTot2011$MCQ160L, mean))
LiverDifference2011PFOS <- exp(diffl11d)
ThyroidDifference2011PFOS

### Confidence Interval
LiverConfInt2011PFOS <- t.test(logLBXPFOS ~ MCQ160L, data = PFAsLiverTot2011)$conf.int
ThyroidConfInt2011PFOS

### Plot
ggplot(data = PFAsLiverTot2011, aes(x = logLBXPFOS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

##################################################

# 2013 Liver Analysis

PFAsLiverYay2013 <- PFAsTotal2013 |>
  filter(MCQ160L == 1) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsLiverNay2013 <- PFAsTotal2013 |>
  filter(MCQ160L == 2) |>
  select(-c(PFARespQs2013, PFAMetaQs2013, PFAEndoQs2013, PFACardQs2013, PFAident2013))

PFAsLiverTot2013 <- PFAsTotal2013 |>
  filter(MCQ160L != 7 & MCQ160L != 9) |>
  mutate(MCQ160L = if_else(MCQ160L == 1, "Yes", "No"))


## FNS
YesLiver2013Summ <- summary(PFAsLiverYay2013)
NoLiver2013Summ <- summary(PFAsLiverNay2013)
YesLiver2013Summ
NoLiver2013Summ


## PFHS
### ANOVA
LiverFits2013PFHS <- aov(logSSPFHS ~ MCQ160L, data = PFAsTotal2013)
summary(LiverFits2013PFHS)

### Mean Difference
diffl13a <- diff(tapply(PFAsLiverTot2013$logSSPFHS, PFAsLiverTot2013$MCQ160L, mean))
LiverDifference2013PFHS <- exp(diffl13a)
LiverDifference2013PFHS

### Confidence Interval
LiverConfInt2013PFHS <- t.test(logSSPFHS ~ MCQ160L, data = PFAsLiverTot2013)$conf.int
LiverConfInt2013PFHS

### Plot
ggplot(data = PFAsLiverTot2013, aes(x = logSSPFHS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA (SSPFNA)
### ANOVA
LiverFits2013PFNA <- aov(logSSPFNA ~ MCQ160L, data = PFAsTotal2013)
summary(LiverFits2013PFNA)

### Mean Difference
diffl13b <- diff(tapply(PFAsLiverTot2013$logSSPFNA, PFAsLiverTot2013$MCQ160L, mean))
LiverDifference2013PFNA <- exp(diffl13b)
LiverDifference2013PFNA

### Confidence Interval
LiverConfInt2013PFNA <- t.test(logSSPFNA ~ MCQ160L, data = PFAsLiverTot2013)$conf.int
LiverConfInt2013PFNA

### Plot
ggplot(data = PFAsLiverTot2013, aes(x = logSSPFNA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (SSBFOA)
### ANOVA
LiverFits2013BFOA <- aov(logSSBFOA ~ MCQ160L, data = PFAsTotal2013)
summary(LiverFits2013BFOA)

### Mean Difference
diffl13c <- diff(tapply(PFAsLiverTot2013$logSSBFOA, PFAsLiverTot2013$MCQ160L, mean))
LiverDifference2013BFOA <- exp(diffl13c)
LiverDifference2013BFOA

### Confidence Interval
LiverConfInt2013BFOA <- t.test(logSSBFOA ~ MCQ160L, data = PFAsLiverTot2013)$conf.int
LiverConfInt2013BFOA

### Plot
ggplot(data = PFAsLiverTot2013, aes(x = logSSBFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (SSMFOS) & n-PFOA (SSNFOA) are both the same for every individual.


##################################################

# 2015 Liver Analysis

PFAsLiverYay2015 <- PFAsTotal2015 |>
  filter(MCQ160L == 1) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsLiverNay2015 <- PFAsTotal2015 |>
  filter(MCQ160L == 2) |>
  select(-c(PFARespQs2015, PFAMetaQs2015, PFAEndoQs2015, PFACardQs2015, PFAident2015))

PFAsLiverTot2015 <- PFAsTotal2015 |>
  filter(MCQ160L != 7 & MCQ160L != 9) |>
  mutate(MCQ160L = if_else(MCQ160L == 1, "Yes", "No"))


## FNS
YesLiver2015Summ <- summary(PFAsLiverYay2015)
NoLiver2015Summ <- summary(PFAsLiverNay2015)
YesLiver2015Summ
NoLiver2015Summ


## PFHS
### ANOVA
LiverFits2015PFHS <- aov(logLBXPFHS ~ MCQ160L, data = PFAsTotal2015)
summary(LiverFits2015PFHS)

### Mean Difference
diffl15a <- diff(tapply(PFAsLiverTot2015$logLBXPFHS, PFAsLiverTot2015$MCQ160L, mean))
LiverDifference2015PFHS <- exp(diffl15a)
LiverDifference2015PFHS

### Confidence Interval
LiverConfInt2015PFHS <- t.test(logLBXPFHS ~ MCQ160L, data = PFAsLiverTot2015)$conf.int
LiverConfInt2015PFHS

### Plot
ggplot(data = PFAsLiverTot2015, aes(x = logLBXPFHS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## PFNA
### ANOVA
LiverFits2015PFNA <- aov(logLBXPFNA ~ MCQ160L, data = PFAsTotal2015)
summary(LiverFits2015PFNA)

### Mean Difference
diffl15b <- diff(tapply(PFAsLiverTot2015$logLBXPFNA, PFAsLiverTot2015$MCQ160L, mean))
LiverDifference2015PFNA <- exp(diffl15b)
LiverDifference2015PFNA

### Confidence Interval
LiverConfInt2015PFNA <- t.test(logLBXPFNA ~ MCQ160L, data = PFAsLiverTot2015)$conf.int
LiverConfInt2015PFNA

### Plot
ggplot(data = PFAsLiverTot2015, aes(x = logLBXPFNA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sb-PFOA (BFOA)
### ANOVA
LiverFits2015BFOA <- aov(logLBXBFOA ~ MCQ160L, data = PFAsTotal2015)
summary(LiverFits2015BFOA)

### Mean Difference
diffl15c <- diff(tapply(PFAsLiverTot2015$logLBXBFOA, PFAsLiverTot2015$MCQ160L, mean))
LiverDifference2015BFOA <- exp(diffl15c)
LiverDifference2015BFOA

### Confidence Interval
LiverConfInt2015BFOA <- t.test(logLBXBFOA ~ MCQ160L, data = PFAsLiverTot2015)$conf.int
LiverConfInt2015BFOA

### Plot
ggplot(data = PFAsLiverTot2015, aes(x = logLBXBFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## Sm-PFOS (MFOS)
### ANOVA
LiverFits2015MFOS <- aov(logLBXMFOS ~ MCQ160L, data = PFAsTotal2015)
summary(LiverFits2015MFOS)

### Mean Difference
diffl15d <- diff(tapply(PFAsLiverTot2015$logLBXMFOS, PFAsLiverTot2015$MCQ160L, mean))
LiverDifference2015MFOS <- exp(diffl15d)
LiverDifference2015MFOS

### Confidence Interval
LiverConfInt2015MFOS <- t.test(logLBXMFOS ~ MCQ160L, data = PFAsLiverTot2015)$conf.int
LiverConfInt2015MFOS

### Plot
ggplot(data = PFAsLiverTot2015, aes(x = logLBXMFOS, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)


## n-PFOA (NFOA)
### ANOVA
LiverFits2015NFOA <- aov(logLBXNFOA ~ MCQ160L, data = PFAsTotal2015)
summary(LiverFits2015NFOA)

### Mean Difference
diffl15e <- diff(tapply(PFAsLiverTot2015$logLBXNFOA, PFAsLiverTot2015$MCQ160L, mean))
LiverDifference2015NFOA <- exp(diffl15e)
LiverDifference2015NFOA

### Confidence Interval
LiverConfInt2015NFOA <- t.test(logLBXNFOA ~ MCQ160L, data = PFAsLiverTot2015)$conf.int
LiverConfInt2015NFOA

### Plot
ggplot(data = PFAsLiverTot2015, aes(x = logLBXNFOA, fill = MCQ160L)) + 
  scale_fill_manual(values = c("#0072B2", "#E69F00", "#009E73")) +
  geom_density(alpha = 0.4)

```

## Logistic Regression Models

We could do this by year and have different confounding variables found in each one.

```{r}

```

## CB-SEM and PCA

```{r}

```

## Neural Network

```{r}

```

### TDA?

```{r}

```


>>>>>>> 5ac0bc8572beaae8a9c4eaa56fa871a51a2c2a78
